### 2024-03-16 sc-curve-config.tex
Add files via upload

\documentclass[12pt,reqno]{amsart}
%\usepackage[small,nohug,heads=vee]{diagrams}
%\diagramstyle[labelstyle=\scriptstyle]

\usepackage{hyperref}
\usepackage{amsthm, amsmath, amscd, amssymb,centernot}
\usepackage{amsfonts}
\usepackage[all]{xy}
\usepackage{comment}
%\usepackage{palatino,eulervm}
\usepackage[T1]{fontenc}
\usepackage[left=2.5cm,top=2.5cm,bottom=3cm,right=2.5cm]{geometry}
%\usepackage[pagewise]{lineno}\linenumbers
\setlength{\headheight}{15.2pt}

\usepackage{graphicx}
\usepackage{tikz-cd}
\usepackage{epsf}
\usepackage{float}

%\usepackage{etoolbox}
%\makeatletter
%\patchcmd{\@settitle}{\uppercasenonmath\@title}{}{}{}
%\patchcmd{\@setauthors}{\MakeUppercase}{}{}{}
%patchcmd{\section}{\scshape}{}{}{}
%\makeatother
\makeatletter
\@namedef{subjclassname@2020}{%
\textup{2020} Mathematics Subject Classification}
\makeatother

\setlength\parskip{.1in}
\setlength\parindent{0.2in}
%%% Environments

\newcommand{\naturals}{\mathbb N}
\newcommand{\ints}{\mathbb Z}
\newcommand{\rationals}{\mathbb Q}
\newcommand{\reals}{\mathbb R}
\newcommand{\product}{\prod_{\alpha} X_{\alpha}}
\newcommand{\coll}{\mathcal{C}}
\newcommand{\str}{\mathcal{O}}
\newcommand{\g}{\mathbb{G}}
\newcommand{\proj}{\mathbb{P}}
\newcommand{\aff}{\mathbb{A}}
\newcommand{\complex}{\mathbb C}
\newcommand{\li}{\mathcal L}
\newcommand{\s}{\varepsilon}
\theoremstyle{plain}
\numberwithin{equation}{section}
\newtheorem{theorem}{Theorem}[section]
\newtheorem*{theorem*}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
%\newtheorem{definition}[theorem]{Definition}
\theoremstyle{definition}
\newtheorem{question}[theorem]{Question}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}
\newtheorem{discussion}[theorem]{Discussion}
\newtheorem{assumption}[theorem]{Assumption}
\usepackage{xcolor}

%\newcommand\npara{
	%\setlength{\parindent}{0.2in}
	%	\setlength{\parskip}{0.1in}
	%}
%\newcommand\thmpara{
	%	\setlength{\parindent}{0in}
	%	\setlength{\parskip}{0.1in}
	%}
\begin{document}
	\title[Seshadri constants  of curve configurations on surfaces]{Seshadri constants  of curve configurations on surfaces}
	\author[K. Hanumanthu]{Krishna Hanumanthu}

\address{Chennai Mathematical Institute, H1 SIPCOT IT Park, Siruseri, Kelambakkam 603103,
India.}

\email{krishna@cmi.ac.in}

\author[P. K. Roy]{Praveen Kumar Roy}

\address{UM-DAE Centre for Excellence in Basic Sciences
"Nalanda", Opp Nano Sciences Building,
University of Mumbai, Vidyanagari,
Mumbai 400098, India.}

\email{praveen.roy@cbs.ac.in}

\author[A. Subramaniam]{Aditya Subramaniam}

\address{Indian Institute of Science Education and Research Tirupati, Rami Reddy Nagar, Karakambadi Road, Mangalam (P.O.)
Tirupati, Andhra Pradesh, INDIA – 517507.}

\email{adityasubramaniam@labs.iisertirupati.ac.in}
\subjclass[2020]{14C20,14N10, 14N20}

\keywords{Seshadri constants,  transversal curve arrangements, configurational Seshadri constants}

\date{\today}

	\begin{abstract}
	Let $X$ be a complex nonsingular projective surface and let $L$ be an ample line bundle on $X$. We study multi-point Seshadri constants of $L$ at singular points of certain arrangements of curves on $X$. We pose some questions about such Seshadri constants and prove some results in the case of star arrangements of curves. We also study the configurational Seshadri constants for curve arrangements on surfaces and compare them with the usual Seshadri constants. We give several examples illustrating the properties that we study. 
	\end{abstract}

		\maketitle

	\section{Introduction}
	In this note, we study multi-point Seshadri constants of ample line bundles centered at the singular loci of certain curve arrangements on surfaces. We recall the notion of  multi-point Seshadri constants briefly below.

	Let $X$ be a smooth complex projective variety and let $L$ be a nef line bundle on
	$X$. Let $r \ge 1$ be an integer and let $x_1,\ldots,x_r$ be distinct
	points of $X$.
	The {\it Seshadri constant} of $L$ at $x_1,\ldots,x_r \in X$ is defined as: 
	$$\varepsilon(X,L,x_1,\ldots,x_r):=  \inf\limits_{\substack{C \subset
			X{\rm ~a~ curve~ with} \\C \cap \{x_1,\ldots,x_r\}
			\ne \emptyset}} \frac{L\cdot C}{\sum\limits_{i=1}^r {\rm
			mult}_{x_i}C}.$$

	It is easy to see that the infimum above is the same as the infimum taken over
	irreducible, reduced curves $C$ such that $C \cap \{x_1,\ldots,x_r\}
	\ne \emptyset$.

	The following is a  well-known upper bound for Seshadri
	constants. 
	Let $n$ be the dimension of $X$. Then for
	any $x_1,\ldots,x_r \in X$, 
	\begin{eqnarray*}\label{wellknown}
		\varepsilon(X,L,x_1,\ldots,x_r) \le
		\sqrt[n]{\frac{L^n}{r}}.
	\end{eqnarray*}
	The study of multi-point Seshadri constants is interesting even in the case of the projective plane $\mathbb{P}^2.$ A famous conjecture of Nagata asserts that if $r \geq 10$ and $x_1,\cdots, x_r \in \mathbb{P}^2 $ are very general, then 
	$$\varepsilon(\mathbb{P}^2,\mathcal{O}_{\mathbb{P}^2}(1),x_1,\ldots,x_r)= \frac{1}{\sqrt{r}}.$$ 
	Nagata \cite{Nag} proved this when $r=s^2$ for an integer $s$, but it is open in all other cases.

	On the other hand, when the points $x_1, \cdots, x_r$ lie in special position, the corresponding  Seshadri constant is frequently rational, and it is a very interesting problem to compute it. For example, if the points are collinear then 
	$\varepsilon(X,L,x_1,\ldots,x_r) = \frac{1}{r}$.

	In this direction, the author in \cite{Pok} considers behaviour of multi-point Seshadri constants  
	of $\mathcal{O}_{\mathbb{P}^2}(1)$ at the 
	set of singular points  of a line configuration in the plane $\mathbb{P}^2.$  The following 
	question was posed in \cite{Pok}.

		\begin{question}\label{qn1}
		Let $x_1, \cdots, x_r \subset \mathbb{P}^2$ be the set of singular points in a configuration of lines  which is not a pencil of lines. Let $k$ denote the maximum number of points which lie on a line. Is it true that 
		$$\varepsilon(\mathbb{P}^2,\mathcal{O}_{\mathbb{P}^2}(1),x_1,\ldots,x_r)= \frac{1}{k} ? $$
	\end{question}
	In \cite{Pok}, the author gives specific examples like line arrangements satisfying \textit{Hirzebruch's property} and star arrangement of $d$ lines in $\mathbb{P}^2$ where there is an affirmative answer to the above question. 
	In \cite{JP}, the authors extend the above study to the case of arrangements of plane curves of a fixed degree. These arrangements were introduced in the context of Harbourne constants in \cite{PRS} and the bounded negativity conjecture. In order to study the  local negativity phenomenon for algebraic surfaces, it was more reasonable to consider curve arrangements instead of irreducible curves as they are more difficult to construct.

	In \cite{JP}, the authors also study the multi-point Seshadri constants of $\mathcal{O}_{\mathbb{P}^{2}_{\mathbb{C}}}(1)$ centered at singular loci of certain curve arrangements $\mathcal{C}$ in ${\mathbb{P}^{2}_{\mathbb{C}}}$ using a combinatorial invariant called the  \textit{configurational Seshadri constant of $\mathcal{C}$}. They give lower bounds for the configurational Seshadri constants of $\mathcal{O}_{\mathbb{P}^{2}_{\mathbb{C}}}(1)$ and also provide some actual values of the multi-point Seshadri constants for some classes of curve arrangements, comparing them with their associated configurational Seshadri constants.

In this paper, we continue this study by looking at curve arrangements on arbitrary surfaces. We prove some analogues of the results in \cite{JP} for arbitrary surfaces. We work over the field of complex numbers.

We recall below the basic definitions that we require in this paper.

	\begin{definition}[Transversal arrangement]
		Let $\mathcal{C}=\{C_1,C_2, \ldots ,C_d\}$ be an arrangement of curves
		on a smooth projective surface $X$.
		We say that $\mathcal{C}$ is a \emph{transversal arrangement}
		if $d\geq 2$, all  curves $C_i$ are smooth, irreducible 
		and they intersect pairwise transversally.
	\end{definition}

	Let $\text{Sing}(\mathcal{C})$ be the set of all intersection points
	of the curves in a transversal arrangement $\mathcal{C}$. 
	Let $s$ denote the number of points in $\text{Sing}(\mathcal{C})$.

	\begin{definition}[Combinatorial invariants of transversal arrangements]
		Let	$\mathcal{C}$ be a transversal arrangement on a smooth surface
		$X$. For a point $p\in X,$
		let $r_p$ denote the  number of elements of $\mathcal{C}$ that pass
		through $p$. We call $r_p$ the \textit{multiplicity} of $p$ in
		$\mathcal{C}.$ We say $p$ is a $k$-fold point of $\mathcal{C}$ 
		if there are exactly $k$ curves in $\mathcal{C}$ passing through $p.$
		For a positive integer $k\geq2$, $t_k$ denotes the number of $k$-fold points in $\mathcal{C}$.
	\end{definition}
	These numbers satisfy the following standard equality, which follows by
	counting incidences in a transversal arrangement in two ways:
	\begin{equation}\label{eq:combinatorial general}
		\sum_{i<j}(C_i\cdot C_j)=\sum_{k\geq 2}\binom{k}{2}t_k.
	\end{equation}
	Also, let $$f_i=f_i(\mathcal C) :=\sum_{k\geq 2}k^i t_k.$$
	In particular, $f_0=s$ is the number of points in
	$\text{Sing}(\mathcal{C})$.

	\begin{definition}
		Let $\mathcal{C}=\{C_1,C_2, \ldots ,C_d\}$ be an arrangement of irreducible curves
		on a smooth projective surface $X$ and singular locus $\text{Sing}(\mathcal{C}).$ Let $L$ be an ample line bundle on $X$. We define the \textit{configurational Seshadri constant} of $\mathcal{C}$ as 
%		\begin{equation*}
			$$\varepsilon_\mathcal{C}(L):= \frac{\sum\limits_{i=1}^{d}L\cdot C_i}{\sum\limits_{p \in \text{Sing}(\mathcal{C}) }\text{mult}_p(\mathcal{C})}.$$
%		\end{equation*}
	\end{definition}

%\textcolor{blue}{Give some motivation for star arrangements.}

The main configurations considered in this paper are the \textit{star configurations}. We make the following definition: 
\begin{definition} Let $X$ be a nonsingular projective surface.  
A transversal arrangement of curves $\mathcal{C}$ on $X$
		 is called a \emph{star  configuration} if the only intersection points are double points.
	\end{definition}

If $\mathcal{C}= \{C_1,C_2, \ldots ,C_d\}$ is a star arrangement and $C_i$ are linearly equivalent to each other then $$t_2=\frac{C_1^2d(d-1)}{2}\text{ and }t_k = 0 \text{ for } k > 2.$$

Star configurations of lines in $\mathbb{P}^2$, and more generally of hyperplanes in $\mathbb{P}^n$, are extensively studied; 
see \cite{CV,GHM, JP}, for some results.

In Section \ref{main}, we prove our main result (Theorem \ref{prop:star}) for star arrangements of curves on arbitrary surfaces. 
In Section \ref{ruled}, we consider some examples on ruled surfaces. In Section \ref{compare}, we compare the usual Seshadri constants with configurational Seshadri constants. In Section \ref{bounds}, we give lower bounds for configurational Seshadri constants for curve arrangements on surfaces. 
Finally, we give an example of a computation of multi-point Seshadri constant at the singular locus of an arrangement of curves on a K3 surface.

	\section{Seshadri constants for certain transversal curve arrangements}\label{main}	
	%\subsection{General results for any surface}
	We work with curve configurations on surfaces satisfying the following assumption. 
	\begin{assumption}\label{star1}
		Let $\mathcal{C}=\{C_1,C_2, \ldots ,C_d\}$, $d\geq 4$ be a transversal arrangement of curves
		on a complex smooth projective surface $X$ with the following properties: 
		\begin{itemize}
			\item There is no point where all the curves meet, i.e., $t_d=0.$
			\item  All the curves $C_i$ in $\mathcal{C}$ are linearly equivalent to a
			fixed divisor $A$ on $X$.
		\end{itemize}
	\end{assumption}

	\begin{definition}
		Let $\mathcal{C}$ be a transversal arrangement of curves on a smooth projective surface $X$
		satisfying Assumption \ref{star1}. Then we define the \emph{base constant} of $\mathcal{C}$ as 
		$${\rm bs}(\mathcal{C}) := {\rm max} \{t \, | \, t = \# \, C_{i} \cap {\rm Sing}(\mathcal{C}), \, C_{i} \in \mathcal{C}\},$$
		i.e., ${\rm bs}(\mathcal{C})$ is equal to the maximum number of singular points  of $\mathcal{C}$ that are contained in a single curve $C_{i} \in \mathcal{C}$.
	\end{definition}

The following question is a generalization of Question \ref{qn1} to curve arrangements on arbitrary surfaces.

	\begin{question}\label{question}
		Let $\mathcal{C} =\{C_1,C_2, \ldots ,C_d\}$ be a transversal arrangement of curves on a smooth projective surface $X$
		satisfying Assumption \ref{star1}. Let $L$ be an ample line bundle on $X$. Is it true that
		\begin{equation*}\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \frac{L \cdot C_1}{{\rm bs}(\mathcal{C})}?
		\end{equation*}
	\end{question}

By \cite[Example 3.5]{JP}, the above question has a negative answer for the Hesse arrangement of conics 
in $\mathbb{P}^2$. However it is open for line arrangements in $\mathbb{P}^2$. 
It is interesting to study the situations in which it is true on arbitrary surfaces.

For an arbitrary curve arrangement $\mathcal{C}$ satisfying Assumption \ref{star1}, the base constant is at most 
$C_1^2(d-1)$. So the following question arises naturally.

	\begin{question}\label{QuestM}
		Let $\mathcal{C} =\{C_1,C_2, \ldots ,C_d\}$ be a transversal arrangement of curves on a smooth projective surface $X$
		satisfying Assumption \ref{star1}. Let  ${\rm Sing}(\mathcal{C})$ denote the singular locus of $\mathcal{C}$ and let $L$ be an ample line bundle on $X$. Is it true that
		\begin{equation}\label{ques}
			\varepsilon(X, L,{\rm Sing}(\mathcal{C})) \geq \frac{L \cdot C_1}{C_1^2(d-1)} ?	
		\end{equation}

	\end{question}

	For star arrangements, the base constant is exactly equal to $C_1^2(d-1)$.
	We now show that the lower bound in Question \ref{QuestM} can be achieved by certain star configuration of curves on $X.$	So Question \ref{question} has an affirmative answer for these star arrangements.

	\begin{theorem}
		\label{prop:star} Let $X$ be a nonsingular projective surface and let $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ be a star configuration of curves on $X$ with $d \geq 4$ such that each $ C_i$ is linearly equivalent to a fixed divisor $A$ on $X$. Let $L$ be an ample line bundle on $X$
		such that  $\frac{dC_1^2}{(d-1)(L\cdot C_1)}L-C_1$ is nef.   Then 
		$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \frac{L\cdot C_1}{C_1^2(d-1)}.$$
	\end{theorem}
	\begin{proof}
	 Let $\mathcal{P} = \{p_{1}, \ldots, p_{s}\}$ be the singular locus of  $\mathcal{C}$. Note that $p_{1}, \ldots, p_{s}$ are all double points of 
	  $\mathcal{C}$. Exactly $C_1^2(d-1)$ of these points lie on $C_1$. So the Seshadri ratio computed by $C_1$ is precisely 
	  $ \frac{L\cdot C_1}{C_1^2(d-1)}$. Note that the same ratio is also contributed by each of the curves $C_2,\ldots, C_d$.

	 Suppose that there exists an irreducible and reduced curve $D$, different from $C_{i}$ for $i \in \{1,\ldots, d\}$, having multiplicity $m_{p}(D)$ at each point $p \in \mathcal{P}$ such that
		$$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \frac{L\cdot C_1}{C_1^2(d-1)}.$$
This gives
		$$(\triangle) : \quad (L \cdot D)C_1^2(d-1) < \left(\sum_{p \in \mathcal{P}} m_{p}(D)\right)L\cdot C_1.$$
		By B\'ezout's theorem, we obtain
		\begin{eqnarray*}
		D\cdot (C_{1}+ \ldots + C_{d})=d(D\cdot C_1) &\geq& \sum_{p \in \mathcal{P}}m_{p}(D)\cdot m_{p}(C_{1}+ \ldots + C_{d})\\
		&\stackrel{(*)}{\geq}& 2\sum_{p \in \mathcal{P}} m_{p}(D) \\
		&\stackrel{(\triangle)}{>}& \frac{2(L \cdot D)C_1^2(d-1)}{L\cdot C_1},
		\end{eqnarray*}
		where $(*)$ comes from the fact that all the singular points of $C_{1}+ \ldots + C_{d}$ are at least double points. Now we use the nefness 
		of $\frac{dC_1^2}{(d-1)(L\cdot C_1)}L-C_1$ and note the following  inequality: 
		\[
		\frac{dC_1^2}{(d-1)(L\cdot C_1)}L\cdot D \geq D\cdot C_1.
		\] 
		This leads to the following:
		\begin{eqnarray*}
			\frac{d^2C_1^2}{(d-1)(L\cdot C_1)}L\cdot D &\geq& d (D\cdot C_1) > \frac{2(d-1)(L\cdot D)C_1^2}{L\cdot C_1} \\
			\Rightarrow \frac{d^2C_1^2}{d-1} &>& 2(d-1)C_1^2 \quad \quad \text{(since $L$ is ample)} \\
			\Rightarrow \left(\frac{d}{d-1} \right)^2 &>& 2 \quad \quad \text{(since $C_1^2 = C_1\cdot C_2 > 0$)}.
		\end{eqnarray*}
		This is a contradiction, since $d\geq 4$.
	\end{proof}
	\begin{corollary}
		\label{coro:star}
		If $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ is a star configuration with $d \geq 4$  and $L$ is an ample line bundle on $X$ such that $ C_i \in |mL|$ for all $i$ and a positive integer $m>0$, then 
		$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \frac{1}{m(d-1)}.$$
	\end{corollary}

\begin{remark}
Several authors have studied multi-point Seshadri constants on surfaces; for a sample of results, see \cite{B,HM, HR, PR, RR, SS}. 
Many of these results consider general points. 
Theorem \ref{prop:star} gives a computation of Seshadri constants at \textit{special} points. 
\end{remark}

The proof of Theorem \ref{prop:star} shows that for an arbitrary arrangement, not necessarily a star arrangement, we have the following lower and upper bounds for the Seshadri constants.

\begin{corollary}\label{cor-main}
Let $X$ be a nonsingular projective surface and let $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ be a configuration of curves on $X$ satisfying Assumption \ref{star1}.
%such that each $ C_i$ is linearly equivalent to a fixed divisor $A$ on $X$. 
 Let $L$ be an ample line bundle on $X$
		such that  $\frac{dC_1^2}{(d-1)(L\cdot C_1)}L-C_1$ is nef.   Then
$$\frac{L\cdot C_1}{C_1^2(d-1)} \le \varepsilon(X, L,{\rm Sing}(\mathcal{C})) \le \frac{L \cdot C_1}{{\rm bs} (\mathcal{C})}  .$$
\end{corollary} 
\begin{proof}
The inequality $\frac{L\cdot C_1}{C_1^2(d-1)} \le \varepsilon(X, L,{\rm Sing}(\mathcal{C}))$ follows from the proof of Theorem \ref{prop:star}. Note that for any reduced and irreducible curve $D$ which is not in $\mathcal{C}$, we showed that the Seshadri ratio is at least $\frac{L\cdot C_1}{C_1^2(d-1)}$ and this part does not use the fact that $\mathcal{C}$ is a star arrangement.

For curves in $\mathcal{C}$, the least Seshadri ratio is  $\frac{L \cdot C_1}{\rm{bs} (\mathcal{C})}$. 
Since we always have ${\rm bs} (\mathcal{C}) \le C_1^2(d-1)$, the proof is complete. 
\end{proof}

\begin{example}
Consider the Hesse arrangement $\mathcal{C} = \{C_1, \ldots, C_{12}\}$  of conics in $\mathbb{P}^2$
which has 21 singular points.  The base constant of $\mathcal{C}$  is 8.  
 The Seshadri constant of $L = \mathcal{O}_{\mathbb{P}^2}(1)$ at these 21 points is known to be $\frac{1}{5}$; see \cite[Example 3.5]{JP}.

It is easy to see that $\frac{24}{11}L - C_1$ is nef. 
Then Corollary \ref{cor-main} implies
$$\frac{1}{22} <  \varepsilon(\mathbb{P}^2, L,{\rm Sing}(\mathcal{C})) = \frac{1}{5}<  \frac{1}{4}.$$

This shows that the inequalities in Corollary \ref{cor-main} are strict, in general. In particular,  Theorem \ref{prop:star} does not hold in this case. Note that $\mathcal{C}$ is not a star arrangement.

\end{example}

\begin{example}
		Let $\mathcal{L}_n \subset \mathbb{P}^2$ denote the $n$-th Fermat arrangement of $3n$ lines $l_i$ with $n \geq 3$ given by the linear factors of the polynomial 
		\[
		Q(x,y,z)=(x^n-y^n)(y^n-z^n)(z^n-x^n).
		\]
		It is well known that it has $n^2$ (say $\{p_1,\ldots,p_{n^2}\}$) triple points and $3$ points of multiplicity $n$ (say $\{q_1,q_2,q_3\}$); see \cite[Example II.6]{U}.  We now consider a 
		curve $C$ of degree $6$ not passing through either $p_i$ or $q_j$ and take the double cover 
				$\pi : X \longrightarrow \mathbb{P}^2$
		branched along $C$. Then $X$ is a K3 surface  and $L : = \pi^*(\mathcal{O}(1))$ is ample.

For each $i$, let $C_i$ denote the inverse image of $l_i$ and let 
$\mathcal{C}_n := \{C_1,\ldots, C_{3n}\}$ be an arrangement of curves on $X$. Note that $C_i^2 = 2$ for every $i$ and 
$C_i$ is linearly equivalent to $C_j$ for all $i,j$. 
One can check that the base constant of the arrangement $\mathcal{C}_n$ is $2n+2$.

It is easy to see that this arrangement satisfies the hypotheses of Corollary \ref{cor-main}. 
So we have the following inequalities:
$$\frac{1}{3n-1} \le \varepsilon(X, L,{\rm Sing}(\mathcal{C}_n)) \le \frac{1}{n+1}.$$

%It is easy to see that this arrangement satisfies the hypotheses of Theorem \ref{prop:star}. Hence we conclude that 
%\[
%		\varepsilon(X, L,\text{Sing}(\mathcal{L}_n)) = \frac{L \cdot C_1}{C_1^2(3n-1)} = \frac{1}{3n-1}.
%		\]

\end{example}

	We now construct examples such that the conclusion of Theorem \ref{prop:star} holds, even without the nefness condition in the hypothesis. We construct these examples by obtaining transversal arrangement of curves on rational ruled surfaces coming from line arrangements in $\mathbb{P}^2.$

\subsection{Examples on ruled surfaces}\label{ruled}

	We first recall some basic facts about ruled surfaces. We follow the notation of \cite[Chapter V, Section 2]{Har}.

	Let $C$ be a smooth complex curve of genus $g$ and let $\pi: X \to C$ be a ruled surface over $C$. We choose a normalized vector bundle $E$ of rank 2 on $C$ such that $X = \proj_C(E)$. Let $e :=-\text{deg}(E)$. Let $C_0$ be the image of a section of $\pi$ such that $C_0^2 = -e$ and let $f$ be a fiber of $\pi$. Then the Picard group of $X$ modulo numerical equivalence is a free abelian group of rank 2 generated by $C_0$ and $f$. We have $C_0\cdot f=1$ and $f^2 =0$.

	A complete characterization of ample line bundles and irreducible curves on $X$ is known. For this, and other details on ruled surfaces, we refer to \cite[Chapter V, Section 2]{Har}.

	%{\bf Construction of arrangements on rational ruled surfaces:} \\	
	Let $X = X_e \to \mathbb{P}^1$ be a rational ruled surface with invariant $e \ge 1$. 
	Given a line arrangement in $\proj^2$, one can obtain an arrangement of
	curves on $X_e$, following a construction outlined in \cite[Example
	15]{E}, where a specific finite morphism $X_e \to X_1$ of degree $e$ is described. Note
	that $X_1$ is isomorphic to a blow up of $\proj^2$ at a point. So we
	can pull-back lines in $\proj^2$ to $X_e$ which are in the class 
	$(1,e)$. If $\mathcal{L}$ is a line arrangement of $d$ lines in the plane, its
	pull-back gives a curve arrangement $\mathcal{C}$ of $d$ curves in
	$X_e$. 
	%The multiplicity of a singular point in the line
	%arrangement is multiplied by $e$ in the curve arrangement in $X$.

	To be more precise, suppose that $\mathcal{L}$ has $s$ singularities 
	and $t_k$ denotes the number of singular points of $\mathcal{L}$ of
	multiplicity $k$. Then the singular points of $\mathcal{C}$ are
	precisely the pre-images of singularities of $\mathcal{L}$. So 
	$\mathcal{C}$  has $es$ singular points and the
	number of singular points of multiplicity $k$ is $et_k$. Note that
	each curve in $\mathcal{C}$ is in the class $(1,e)$ and has
	self-intersection $e$.

	In the next example, the conclusion of Theorem \ref{prop:star} holds, even without the nefness condition in the hypothesis. 
	\begin{example}\label{nef}
		Consider a transversal arrangement $\mathcal{C} = \{C_{1}, \ldots, C_{5}\}$ of curves on a rational ruled surface $X=X_e$ with invariant $e=2$ such that $ C_i \in |C_0+2f|$ and such that the only intersection points are ordinary double points. This configuration can be obtained as pullback of a star configuration of lines from $\mathbb{P}^2$, using the above construction. Note that each $C_i$ contains exactly $(5-1)e=8$ double points from the arrangement.

 Let $L=C_0+3f$ be an ample line bundle on $X.$ Then we have $$(5C_1^2/4L\cdot C_1))L-C_1= \frac{1}{6}(-C_0+3f),$$ which is not nef as $(-C_0+3f)\cdot f = -1 < 0.$ Hence the nefness hypothesis in Theorem \ref{prop:star} fails.

		We now verify that 
		$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \frac{L\cdot C_1}{4C_1^2}=\frac{3}{8}.$$

		Let $\mathcal{P} = \{p_{1}, \ldots, p_{20}\}$ denote the set of all the singular points of $\mathcal{C}$. Suppose that there exists an irreducible and reduced curve $D$, different from each $C_{i}$ for $i \in \{1,\ldots, 5\}$, having multiplicity $m_{p}(D)$ at each point $p \in \mathcal{P}$ such that
		\begin{equation}\label{eg ineq}
			\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \frac{3}{8}.
		\end{equation}
		Using B\'ezout's theorem, we have
		\begin{eqnarray*}
		D\cdot (C_{1}+ \ldots + C_{5})=5(D\cdot C_1) &\geq& \sum_{p \in \mathcal{P}}m_{p}(D)\cdot m_{p}(C_1+\ldots+C_5)\\&=& 2\sum_{p \in \mathcal{P}} m_{p}(D)\\&>&\frac{16(L \cdot D)}{3}.\end{eqnarray*}

		Since $C_1$ is linearly equivalent to $L-f$ and $f$ is nef,  we have $$5(D \cdot L) \geq 5(D \cdot C_{1})> \frac{16(L \cdot D)}{3} ,$$ which is absurd since $L$ is ample.

	\end{example}

	\begin{example}\label{Hirz}
		We now construct examples where the inequality in Equation \ref{ques} is a strict inequality. Consider a transversal arrangement $\mathcal{C}_n = \{C_{1}, \ldots, C_{3n}\}$ of curves on a rational ruled surface $X=X_e$ with invariant $e\ge n>1$ such that $ C_i \in |C_0+ef|$ and such that the curves $C_i$ come as a pullback of a line arrangement $\mathcal{L} \subset \mathbb{P}^2$ satisfying Hirzebruch's property and having singular points with multiplicity greater than two, using the above construction, for more details, see \cite{Pok}. Recall that a line arrangement $\mathcal{L} \subset \mathbb{P}^2$ satisfies  Hirzebruch's property if the number of lines is equal to $3n$ for some $n \in \mathbb{Z}_{>0}$ and each line from $\mathcal{L}$ intersects any other line at exactly $n+1$ points.

		Let $L=C_0+(e+1)f$ be an ample line bundle on $X$. We now verify that  
		$$\varepsilon(X, L,{\rm Sing}(\mathcal{C}_n)) = \frac{L\cdot C_1}{e(n+1)}=\frac{e+1}{e(n+1)}.$$
		Note that $\frac{e+1}{e(n+1)} > \frac{e+1}{e(3n-1)}$, which shows that the 
		inequality in Equation \ref{ques} is strict.

		Let $\mathcal{P}$ denote the set of all intersection points of $\mathcal{C}_n$. 
		The Seshadri ratio computed by $C_1$ is precisely $\frac{e+1}{e(n+1)}$. 
		Suppose that there exists an irreducible and reduced curve $D$, different from each $C_{i}$ for $i \in \{1,\ldots, 3n\}$, having multiplicity $m_{p}(D)$ at each point $p \in \mathcal{P}$ such that
		\begin{equation}\label{eg ineq}
			\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \frac{e+1}{e(n+1)}.
		\end{equation}

		Using B\'ezout's theorem, we have
		\begin{eqnarray*}D\cdot (C_{1}+ \ldots + C_{3n})=3n(D\cdot C_1) &\geq& \sum_{p \in \mathcal{P}}m_{p}(D)\cdot m_{p}(C_1+\ldots+C_{3n}) \\ &\geq &3\sum_{p \in \mathcal{P}} m_{p}(D)\\ &>&\frac{3(L \cdot D)e(n+1)}{e+1}.\end{eqnarray*}

		Since $C_1$ is linearly equivalent to $L-f$ and $f$ is nef,  we have $$3n(D \cdot L) \geq 3n(D \cdot C_{1})>\frac{3(L \cdot D)e(n+1)}{e+1},$$ which is not possible since $e \ge n$ by the choice of $e$.

	\end{example}

	\begin{example}\label{KCW}
		There are examples of line arrangements in $\mathbb{P}^2$ satisfying Hirzebruch's property and such that all the singular points have multiplicity greater than two; for more details, see \cite{Pok}.

		First, we consider the $n$-th Fermat arrangement $\mathcal{L}_n $ of lines  in $\mathbb{P}^2$  with $n \geq 3$. %given by the linear factors of the polynomial
		%$$Q(x,y,z)=(x^n-y^n)(y^n-z^n)(z^n-x^n).$$ 
		As noted above, this arrangement consists of $3n$ lines with $t_n=3$ and $t_3=n^2.$ Note that $\mathcal{L}_n$ satisfies Hirzebruch property. Using the above construction, we can pullback $\mathcal{L}_n$ to a curve arrangement  $\mathcal{C}_n'$ on $X_e$ with $e > n$. Then for the ample line bundle $L=C_0+(e+1)f$ on $X_e$ as in Example \ref{Hirz}, we get
		$$\varepsilon(X_e, L,{\rm Sing}(\mathcal{C}_n')) = \frac{L\cdot C_1}{e(n+1)}=\frac{e+1}{e(n+1)}.$$

		Next,  let $\mathcal{K} $ denote the Klein arrangement of lines consisting of 21 lines in $\mathbb{P}^2$ with $t_4=21$ and $t_3=28.$ Note that $\mathcal{K}$ satisfies Hirzebruch property. Using the above construction, we can pullback $\mathcal{K}$ to a curve arrangement  $\mathcal{K}'$ on $X_e$ with $e > n$ as in the above construction. Then for the ample line bundle $L$ on $X_e$ as in Example \ref{Hirz}, we get
		$$\varepsilon(X_e, L,{\rm Sing}(\mathcal{K}')) = \frac{L\cdot C_1}{e(n+1)}=\frac{e+1}{8e}.$$

		We now consider another arrangement satisfying Hirzebruch property, namely the Wiman arrangement of lines $\mathcal{W}$ in $\mathbb{P}^2$ consisting of 45 lines with $t_3=120$, $t_4=45$ and $t_5=36.$ Using the above construction, we can pullback $\mathcal{W}$ to a curve arrangement  $\mathcal{W}'$ on $X_e$ with $e > n$ as in the above construction. Then for the ample line bundle $L$ on $X_e$ as in Example \ref{Hirz}, we get
		$$\varepsilon(X_e, L,{\rm Sing}(\mathcal{W}')) = \frac{L\cdot C_1}{e(n+1)}=\frac{e+1}{16e}.$$
	\end{example}

	\subsection{Comparing the Seshadri constant and the configurational Seshadri constant} \label{compare}

	We now study possible discrepancies between the configurational and the multi-point Seshadri constants with some examples. It is clear that for an arrangement $\mathcal{C}$ on a smooth projective surface $X$ and an ample line bundle $L,$ we always have the following inequality: 
	$$\varepsilon_\mathcal{C}(L) \geq \varepsilon(X, L,{\rm Sing}(\mathcal{C})).$$
	In general, this inequality is strict. 
	\begin{example}
		In Theorem \ref{prop:star}, we considered a \emph{star} configuration $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ with $d \geq 4$ such that $ C_i \in |A|$ for all $i$, where $A$ was a fixed divisor on $X$. We saw that for an ample line bundle $L$  on $X$, if 
		$\frac{dC_1^2}{(d-1)(L\cdot C_1)}L-C_1$ is nef, the Seshadri constant is given by
		$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \frac{L\cdot C_1}{C_1^2(d-1)}.$$

		On the other hand, the configurational Seshadri constant is given by
		$$	\varepsilon_\mathcal{C}(L)= \frac{d(L\cdot C_1)}{2t_2}= \frac{L\cdot C_1}{C_1^2(d-1)}.$$
		Thus in this case, both these constants agree.
	\end{example}

	\begin{example}
		In Example \ref{KCW}, we first considered a curve arrangement  $\mathcal{C}_n'$ on $X_e$ with $e > n$ obtained as a pullback of the $n$-th Fermat arrangement of lines $\mathcal{L}_n \subset \mathbb{P}^2$  with $n \geq 3.$ This arrangement $\mathcal{C}_n'$ consists of $3n$ curves with $t_n=3e$ and $t_3=en^2.$ Then for the ample line bundle $L=C_0+(e+1)f $ on $X_e$, we obtained the following value of Seshadri constant 
		$$\varepsilon(X_e, L,{\rm Sing}(\mathcal{C}_n')) = \frac{L\cdot C_1}{e(n+1)}=\frac{e+1}{e(n+1)}.$$

		On the other hand, the configurational Seshadri constant is given by
		$$	\varepsilon_{\mathcal{C}_n'}(L)= \frac{3n(L\cdot C_1)}{f_1}= \frac{e+1}{e(n+1)}.$$
		Thus in this case, both these constants agree.

		Next, we considered a curve arrangement  $\mathcal{K}'$ on $X_e$ with $e > n$ which is a pullback of the Klein arrangement of lines $\mathcal{K} \subset \mathbb{P}^2.$ The curve arrangement  $\mathcal{K}'$ consists of 21 curves with $t_4=21e$ and $t_3=28e.$ Then by the choice of an ample line bundle $L$ on $X_e$ as in Example \ref{Hirz}, we obtained the following value of Seshadri constant 
		$$\varepsilon(X_e, L,{\rm Sing}(\mathcal{K}')) = \frac{e+1}{8e}.$$
		On the other hand, the configurational Seshadri constant is given by
		$$	\varepsilon_{\mathcal{K}'}(L)= \frac{21(L\cdot C_1)}{f_1}= \frac{e+1}{8e}.$$
		Thus in this case too both these constants agree.

		We then considered the curve arrangement  $\mathcal{W}'$ on $X_e$ with $e > n$ obtained  as a pullback of the Wiman arrangement of lines $\mathcal{W} \subset \mathbb{P}^2$. The curve arrangement $\mathcal{W}'$ consists of 45 curves with $t_3=120e$, $t_4=45e$ and $t_5=36e.$ Then by the choice of an ample line bundle $L$ on $X_e$ as in Example \ref{Hirz}, we get
		$$\varepsilon(X_e, L,{\rm Sing}(\mathcal{W}')) = \frac{L\cdot C_1}{e(n+1)}=\frac{e+1}{16e}.$$

		On the other hand, the configurational Seshadri constant is given by
		$$	\varepsilon_{\mathcal{W}'}(L)= \frac{45(L\cdot C_1)}{f_1}= \frac{e+1}{16e}.$$
		Thus in this case too both the constants agree.

	\end{example}
We give an example below where the Seshadri constant is strictly smaller than the configurational Seshadri constant. 
\begin{example}
In \cite[Example 3.1]{JP}, it was shown that for a Hirzebruch quasi-pencil $\mathcal{H}$ of $k\geq 4$ lines in $\mathbb{P}^2_{\mathbb{C}}$ with $t_{k-1}=1$ and $t_2=k-1$, the multi-point Seshadri constant $\varepsilon(\mathbb{P}^2_{\mathbb{C}}, \mathcal{O}_{\mathbb{P}^2_{\mathbb{C}}}(1),{\rm Sing}(\mathcal{H}))$ is strictly smaller than its configurational value $\varepsilon_{\mathcal{H}}(\mathcal{O}_{\mathbb{P}^2_{\mathbb{C}}}(1)).$ We can obtain a configuration $\mathcal{H}'$ on a rational ruled surface $X_e$ with $e=k+1$, as a pullback of the Hirzebruch quasi-pencil $\mathcal{H}$, using the construction mentioned above. The configuration $\mathcal{H}'$ consists of $k \geq 4$ curves say $C_{1}, \ldots, C_{k}$, with $t_{k-1}=e$, $t_2=(k-1)e$ and $ C_i \in |C_0+ef|$ for all $i.$ Let $L=C_0+(e+1)f$ be an ample line bundle on $X_e.$

In this case, the configurational Seshadri constant is 
	$$	\varepsilon_{\mathcal{H}'}(L)= \frac{k(L\cdot C_1)}{2e(k-1)+(k-1)e}= \frac{k(e+1)}{3e(k-1)}=\frac{k(k+2)}{3(k^2-1)}.$$

We now claim that 
	$$\varepsilon(X_e, L,{\rm Sing}(\mathcal{H}')) = \frac{e+1}{e(k-1)}=\frac{k+2}{k^2-1}.$$

	Indeed, we can assume that the points of multiplicity $k-1$ are defined by intersections of $C_1, \cdots, C_{k-1}$. Then the curve $C_k$ gives the Seshadri ratio $\frac{e+1}{e(k-1)}=\frac{k+2}{k^2-1}.$  Suppose that there exists an irreducible and reduced curve $D$, different from each $C_{i}$ for each $i$, having multiplicity $m_{p}(D)$ at each point $p \in \mathcal{P}={\rm Sing}(\mathcal{H}')$ such that
	\begin{equation*}
		\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \frac{e+1}{e(k-1)}.		
\end{equation*}

Then 
$$D \cdot (C_1+C_k)=2 (D \cdot C_1) \geq \sum_{p \in \mathcal{P}} m_{p}(D) > \frac{e(k-1)(L \cdot D)}{e+1}.$$
Since $C_1$ is linearly equivalent to $L-f, $ we have $$2(D \cdot L) \geq 2(D \cdot C_{1})> \frac{e(k-1)(L \cdot D)}{e+1},$$ i.e., 
$2(k+2) > k^2-1.$ But this is not possible by the choice of $k$.

	This shows that $\varepsilon_{\mathcal{H}'}(L) > \varepsilon(X_e, L,{\rm Sing}(\mathcal{H}')).$
\end{example}

\subsection{Lower bounds on configurational Seshadri constants}\label{bounds}
We now give some lower bounds on configurational Seshadri constants on ruled surfaces and on surfaces of non-negative Kodaira dimension.

	%\textbf{To be added: mention some notation that we follow about ruled
		%surfaces. }

	\begin{theorem}\cite[Equation 4.9]{HS} \label{HTIn}
		Let $X$ be a ruled surface over a smooth curve of genus $g \geq 0$ with invariant $e
		\ge 4$.  Let $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ be a transversal arrangement of curves
		satisfying Assumption \ref{star1} such that each curve in
		$\mathcal{C}$ is numerically equivalent to $A=aC_0+bf$ with $a > 0$
		and $b \ge ae$. Assume further that either $a\geq 2$ or if $a=1$, there exists a subset of four curves in $\mathcal{C}$ such that there is no point common to all the four curves. Then we have the following Hirzebruch-type inequality for $\mathcal{C}$:\\
		\begin{equation*}\label{eq:Hirzebruch type ineq}
			t_{2}+\frac{3}{4}t_{3} \geq -16+16g+\sum_{k\geq5}(2k-9)t_{k}+
			d(e(5a^2-2a)-10ab-4ag+4a+4b).\\
		\end{equation*}	
	\end{theorem}

	Using the above result, we give a lower bound on configurational Seshadri constants.	
	\begin{theorem} Let $X$ be a ruled surface over a smooth curve of genus $g \geq 0$ with invariant $e
		\ge 4$.  
		Let
$\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$		
		 be a transversal arrangement of curves satisfying hypothesis of Theorem \ref{HTIn} and let $L$ an ample line bundle on $X$. Then 
		$$\varepsilon_{\mathcal{C}}(
		L) \geq \frac{d(L\cdot C_1)}{8-8g+\frac{9(2ab-a^2e)d^2}{4}+\frac{d(2ae-\frac{a^2e}{2}+ab+4ag-4a-4b)}{2}}.$$
	\end{theorem}
	\begin{proof}
		Our strategy is based on the combinatorial features of $\mathcal{C}$. Let us denote $C = C_{1} + \ldots + C_{d}$. Then we can write 
		\begin{equation}
			\varepsilon_\mathcal{C}(L)= \frac{\sum_{i=1}^{d}L\cdot C_i}{\sum_{P \in \text{Sing}(\mathcal{C}) }\text{mult}_P(\mathcal{C})}=\frac{d(L\cdot C_1)}{f_1}.
		\end{equation}

		Our goal here is to find a reasonable upper-bound on the number $f_{1} = \sum_{r\geq 2} rt_{r}$. In order to do so, we are going to use Theorem \ref{HTIn} and Hirzebruch's inequality, namely
		\begin{equation*}\label{eq:Hirzebruch type ineq}
			t_{2}+\frac{3}{4}t_{3} \geq -16+16g+\sum_{k\geq5}(2k-9)t_{k}+
			d(e(5a^2-2a)-10ab-4ag+4a+4b).\\
		\end{equation*}	
		Simplifying this, we get
		\begin{equation*}\label{eq:4.7}
			16-16g+d(2ae-5a^2e+10ab+4ag-4a-4b)+9f_0 \geq2f_1+4t_2 +t_{4} + \frac{9}{4}t_{3}.
		\end{equation*}
		Since $t_{2}, t_{4},t_{3} \geq 0$ we have
		\begin{equation*}\label{eq:4.7}
			16-16g+d(2ae-5a^2e+10ab+4ag-4a-4b)+9f_0 \geq2f_1.
		\end{equation*}
		and hence
		\begin{equation*}\label{eq:4.7}
			8-8g+\frac{d}{2}(2ae-5a^2e+10ab+4ag-4a-4b)+\frac{9}{2}f_0 \geq f_1.
		\end{equation*}
		Obviously one always has $$d \leq f_{0} \leq (2ab-a^2e) {d \choose 2}$$ which leads to
		\begin{equation*}
			f_1 \leq 8-8g+\frac{9(2ab-a^2e)d^2}{4}+\frac{d(2ae-\frac{a^2e}{2}+ab+4ag-4a-4b)}{2},
		\end{equation*}
		so finally we get
		\begin{equation*}
			\varepsilon_\mathcal{C}(L)=\frac{d(L\cdot C_1)}{f_1} \geq \frac{d(L\cdot C_1)}{8-8g+\frac{9(2ab-a^2e)d^2}{4}+\frac{d(2ae-\frac{a^2e}{2}+ab+4ag-4a-4b)}{2}}.
		\end{equation*}		
	\end{proof}

	We will now consider transversal configurations on surfaces of non-negative Kodaira dimension. We will use the following theorem. 
	\begin{theorem}\cite[Theorem 2.1]{LP1} \label{LP}
		Let $X$ be a smooth complex projective surface with non-negative Kodaira dimension and let $C=C_1 + \cdots + C_d$ be a transversal configuration of smooth curves having $d\geq 2$ irreducible components $C_1, \cdots, C_d.$ Then
		\begin{equation*}
			K_X \cdot C + 4 \sum_{i=1}^{d} (1-g(C_i))-t_2+\sum_{r \geq 3} (r-4)t_r \leq 3c_2(X)-K_X^2.
		\end{equation*}
	\end{theorem}
	We now give a lower bound on configurational Seshadri constants on surfaces of non-negative Kodaira dimension.
	\begin{theorem}
		Let $X$ be a smooth complex projective surface with non-negative Kodaira dimension and let $C=C_1 + \cdots + C_d$ be a transversal configuration of smooth curves satisfying Assumption \ref{star1}. Let $L$ be an ample line bundle on $X$. Then
		$$\varepsilon_{\mathcal{C}}(
		L) \geq \frac{d(L\cdot C_1)}{3c_2(X)-K_X^2+4C_1^2 {d \choose 2}-K_X \cdot C-4 \sum_{i=1}^{d} (1-g(C_i))}.$$
	\end{theorem}
	\begin{proof}
		As before, we find an upper-bound on the number $f_{1} = \sum_{r\geq 2} rt_{r}$. In order to do so, we are going to use Theorem \ref{LP} and Hirzebruch's inequality, namely
		\begin{equation*}
			K_X \cdot C + 4 \sum_{i=1}^{d} (1-g(C_i))-t_2+\sum_{r \geq 3} (r-4)t_r \leq 3c_2(X)-K_X^2.
		\end{equation*}
		Simplifying, we get 
		\begin{equation*}
			K_X \cdot C + 4 \sum_{i=1}^{d} (1-g(C_i))+t_2+f_1-4f_0\leq 3c_2(X)-K_X^2.
		\end{equation*}	
		Since $t_2 \geq 0,$ we have 
		\begin{equation*}
			K_X \cdot C + 4 \sum_{i=1}^{d} (1-g(C_i))+f_1-4f_0\leq 3c_2(X)-K_X^2
		\end{equation*}	
		and hence 
		\begin{equation*}
			f_1\leq 3c_2(X)-K_X^2+4f_0-K_X \cdot C-4 \sum_{i=1}^{d} (1-g(C_i)).
		\end{equation*}	
		We know that
			$d \leq f_0 \leq C_1^2 {d \choose 2}$. So 
		\begin{equation*}
			f_1\leq 3c_2(X)-K_X^2+4C_1^2 {d \choose 2}-K_X \cdot C-4 \sum_{i=1}^{d} (1-g(C_i)). 
		\end{equation*}	
		Finally we obtain
		\begin{equation*}
			\varepsilon_\mathcal{C}(L)=\frac{d(L\cdot C_1)}{f_1} \geq \frac{d(L\cdot C_1)}{3c_2(X)-K_X^2+4C_1^2 {d \choose 2}-K_X \cdot C-4 \sum_{i=1}^{d} (1-g(C_i))}.
		\end{equation*}		
	\end{proof}

We end with an example of a configuration of lines on a K3 surface in $\mathbb{P}^3$. Though it does
not fit in the situation studied in this paper (since the curves in the arrangement are not
linearly equivalent to each other), it gives an interesting computation of a multi-point Seshadri
constant on a K3 surface.

\begin{example}
		Let $X \subset \mathbb{P}^3$ be a Fermat quartic defined by the vanishing locus of $x_0^4 + x_1^4 + x_2^4 + x_3^4$, where $x_0, \ldots, x_3$ are the coordinates of $\mathbb{P}^3$. Then $X$ contains the following 48 lines; 16 from each of the following three types: 
		\begin{eqnarray*}
			A: \quad x_0 = \alpha x_1 \; \text{and} \; x_2 = \beta x_3, \\
			A': \quad x_0 = \alpha x_2 \; \text{and} \; x_1 = \beta x_3, \\
			A'': \quad x_0 = \alpha x_3 \; \text{and} \; x_1 = \beta x_2,
		\end{eqnarray*}
		where $\alpha, \beta \in \{\zeta, -\zeta, i\zeta, -i\zeta \}$ and $\zeta$ is a primitive eighth root of unity.

		We describe the intersection behaviour of these lines 
		below.

		First, we consider intersections among lines of type A. 
		If $$A_1: \; x_0 = \alpha x_1, \;  x_2 = \beta x_3 \text{ and } B_1: \; x_0 = \alpha' x_1, \; x_2 = \beta' x_3$$ then 
		\[
		A_1 \cap B_1 \neq \phi \Leftrightarrow x_1 = 0 \;  \text{or} \;  \alpha = \alpha' \; \text{and} \; x_3 = 0\;  \text{or} \; \beta = \beta'.
		\]
		This shows that a line $A_1$ of type $A$ meets three lines of the form  $x_0 = \alpha x_1,\; x_2 = \beta' x_3$ ($\beta' \in \{\zeta, -\zeta, i\zeta, -i\zeta \} \textbackslash \{\beta\}$) of type $A$ at $[\alpha :1 :0 :0]$ and 3 other lines of type $A$ of the form $x_0 = \alpha' x_1,\; x_2 = \beta x_3$ ($\alpha' \in \{\zeta, -\zeta, i\zeta, -i\zeta \} \textbackslash \{\alpha\}$) at $[0 :0 :\beta :1]$.

		On the other hand, a line $A_1$ of type $A$ meets only 4 out of the 16 lines of type $A'$: 
		\[
		A_1 \cap \{x_0 = \alpha' x_2, x_1 = \beta' x_3\} \ne \emptyset
		\]
implies
		%\begin{eqnarray*}
			$x_0 = \alpha' x_2 = \alpha'  \beta x_3 \; \text{and} \; x_0 = \alpha x_1 = \alpha \beta' x_3$. This shows  
			%\Rightarrow 
			$\alpha'  \beta = \alpha \beta'$. Thus the choice of $\beta'$ determines $\alpha'$, giving 4 lines of type $A'$ . Moreover, the intersection point of $A_1$ and a line $\{x_0 = \alpha' x_2, x_1 = \beta' x_3\}$ of type $A'$ 
			is given by $[\alpha \beta'  : \beta' : \beta : 1]$.

			By a similar argument one can see that $A_1$ meets exactly 4 lines of type $A''$.

		Now let $\mathcal{L} = \{l_1,l_2, \ldots,  l_{48}\}$ be the arrangement consisting of all the 48 lines of type $A$, $A'$ and $A''$ on $X$.

		We claim that there exist 24 sets of lines 
		$\mathcal{L}_1$, $\mathcal{L}_2$, \ldots , $\mathcal{L}_{24}$ containing 4 lines each from $\mathcal{L}$
		satisfying the following conditions. Let $1 \le i \le 24$. 
		\begin{itemize}
		\item Each set $\mathcal{L}_i$ contains 4 lines of the same type. 
		\item All the  four lines in each set $\mathcal{L}_i$ meet in one point. 
		\item The divisor obtained by adding the four lines in each  $\mathcal{L}_i$ is linearly equivalent to $\mathcal{O}_X(1)$. 
		\item Each $l_i$ is contained in exactly two of the sets  $\mathcal{L}_1$, $\mathcal{L}_2, \ldots, \mathcal{L}_{24}$. 
	\end{itemize}	
		We will prove that there are 8 sets of the above kind consisting of lines of type $A$. By a similar argument, we get the statement for types $A'$ and $A''$. 
		%We will prove the 
		%claim as well as the construction of $\mathcal{L}_1$, $\mathcal{L}_2$, \ldots, $\mathcal{L}_{24}$ simultaneously. 
		Fix two enumerations of the set $\{\zeta, -\zeta, i\zeta, -i\zeta \}$: $\alpha_1, \alpha_2, \alpha_3, \alpha_4$ and 
$\beta_1, \beta_2, \beta_3, \beta_4$.

First, consider the line $$l_{\alpha_1,\beta_1} = \{x_0 = \alpha_1 x_1 \; \text{and} \; x_2 = \beta_1 x_3\}$$ of type $A$. From the intersection behaviour described above, we know that $l_{\alpha_1,\beta_1}$  meets exactly six lines of type $A$ which are given by: 
		\begin{eqnarray*} 
		l_{\alpha_1,\beta_i}, &\text{ for }& i=2,3,4, \text{ and }\\
		l_{\alpha_j,\beta_1}, &\text{ for } & j=2,3,4.
		\end{eqnarray*}

The four lines $l_{\alpha_1,\beta_1},l_{\alpha_1,\beta_2},l_{\alpha_1,\beta_3},l_{\alpha_1,\beta_4} $ meet at the point 
 $[\alpha_1 :1 :0 :0]$ and the four lines $l_{\alpha_1,\beta_1},l_{\alpha_2,\beta_1},l_{\alpha_3,\beta_1},l_{\alpha_4,\beta_1}$ meet at the point  $[0 :0 :\beta_1 :1]$.

 We define  
 \begin{eqnarray*} 
 \mathcal{L}_{\alpha_1} &=&\{l_{\alpha_1,\beta_1},l_{\alpha_1,\beta_2},l_{\alpha_1,\beta_3},l_{\alpha_1,\beta_4} \},\\ 
\mathcal{L}_{\beta_1} &=& \{l_{\alpha_1,\beta_1},l_{\alpha_2,\beta_1},l_{\alpha_3,\beta_1},l_{\alpha_4,\beta_1} \}.
\end{eqnarray*}

Similarly, we define $\mathcal{L}_{\alpha_i}$ and  $\mathcal{L}_{\beta_j}$ for every 
$2 \le i, j \le 4$.

Note that every line of type $A$ appears in exactly two of the eight sets 
$\mathcal{L}_{\alpha_i}$ and  $\mathcal{L}_{\beta_j}$, where $1\le i, j \le 4$. 
More precisely,  a line $l_{\alpha_i,\beta_j}$ of type $A$ is contained only  in $\mathcal{L}_{\alpha_i}$ and in $ \mathcal{L}_{\beta_j}$.

		%\[
		%\bigcup\limits_{i=1}^{4} \mathcal{L}_{\alpha_i} = \text{Set of all lines of type $A$} = \bigcup\limits_{j=1}^{4} \mathcal{L}_{\beta_j}
		%\]

The collection of these $\mathcal{L}_{\alpha_i}$ and $\mathcal{L}_{\beta_j}$ contribute $8$ sets of lines of type $A$. 
		Similarly we can define $\mathcal{L}_{\alpha_i}'$ and $\mathcal{L}_{\beta_j}'$ from type $A'$ and $\mathcal{L}_{\alpha_i}''$ and $\mathcal{L}_{\beta_j}''$ from type $A''$. This gives a collection of 24 sets which we rename 
		as $\mathcal{L}_1$, $\mathcal{L}_2$, \ldots, $\mathcal{L}_{24}$ such that each $l_i$ is exactly in two of this list.

		We also note that all the lines in $\mathcal{L}_{\alpha_i}$ (respectively, in $\mathcal{L}_{\beta_j}$) lie
		in the hyperplane given by the vanishing of $x_0 - \alpha_i x_1$ (respectively, $x_2 - \beta_j x_3$) in $\mathbb{P}^3$. In fact, the intersection of these hyperplanes with $X$ is precisely the four lines in question. 
		Therefore, for $1 \le i, j \le 4$, 
		\begin{eqnarray*}
		\mathcal{O}_X(1) &\sim&  \; l_{\alpha_i,\beta_1} + l_{\alpha_i,\beta_2} + l_{\alpha_i,\beta_3} + l_{\alpha_i,\beta_4}, \text{ and } \\
		\mathcal{O}_X(1) &\sim& \;  l_{\alpha_1,\beta_j} + l_{\alpha_2,\beta_j} + l_{\alpha_3,\beta_j} + l_{\alpha_4,\beta_j}.
		\end{eqnarray*}

This proves our claim.

		From the intersection behaviour described above, it is clear that the only singular points for the arrangement $\mathcal{L}$ are either double points or quadruple points; \cite[Example 3.3]{Pok1}. It is also not difficult to see that the number of singular points on any line  in $\mathcal{L}$ is 10, as we show now. 
		It suffices to verify this assertion for a line of type $A$. Given a line $l_{\alpha_i,\beta_j}$ of type $A$, we know that it has two quadruple points $[\alpha_i :1 :0 :0]$ and $[0 :0 :\beta_j :1]$. We also know that each line of type $A$ meets 
		4 lines each of type $A'$ and $A''$ and these points are all double points. Therefore in all there are 10 singular points on a line of type $A$. By a similar argument one can show this for lines of type $A'$ and type $A''$ also.

		We now compute the multi-point Seshadri constant of $\mathcal{O}_X(1)$ at the singular locus of 
		the arrangement $\mathcal{L}$.  This arrangement has 216 singular points. So we have 
		$$\varepsilon(X, \mathcal{O}_X(1), \text{Sing}(\mathcal{L})) \le \sqrt{\frac{4}{216}} \sim 0.136.$$

		In fact, we claim that
		\[
		\varepsilon(X, \mathcal{O}_X(1), \text{Sing}(\mathcal{L})) = \frac{1}{10}.
		\]

		Note that each line $l_{\alpha_i,\beta_j}$ has degree 1 in $\mathbb{P}^3$. So,  from the above discussion, it is clear that 
		\[
		\frac{\mathcal{O}_X(1)\cdot l_{\alpha_i,\beta_j}}{10} %= \frac{(l_{\alpha_i,\beta_1} + l_{\alpha_i,\beta_2} + l_{\alpha_i,\beta_3} + l_{\alpha_i,\beta_4})\cdot  l_{\alpha_i,\beta_j} }{10} 
		= \frac{1}{10}.
		\]
		Now let $C \subset X$ be any reduced and irreducible curve such that $C \notin \mathcal{L}$ and which passes through some point in the singular locus of 
		$\mathcal{L}$. By B\'ezout's theorem, we have the following inequality for every line $l \in \mathcal{L}$:
		$$C \cdot l \ge \sum_{p \in l \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C.$$

		We now sum such inequalities over all the 24 sets constructed above. Each such set contributes $C\cdot \mathcal{O}_X(1) = \text{deg}(C)$ to the left hand side. On the right hand side, each line appears twice. Since each double point appears in two lines and each quadruple point appears in four lines, we obtain 
			\begin{eqnarray*}
				24 \text{deg}(C) &\geq& 2 \left(2\sum\limits_{p_i \in \text{Sing}_2(\mathcal{L})} \text{mult}_{p_i} C ~+~ 4\sum\limits_{q_j \in \text{Sing}_4(\mathcal{L})} \text{mult}_{q_j}C \right) \\
		 &\geq& 4 \sum\limits_{p \in\text{Sing}(\mathcal{L})} \text{mult}_{p}C.
		\end{eqnarray*}

		%%%%%
		\iffalse
		Using the sets  $\mathcal{L}_1$, $\mathcal{L}_2$, \ldots, $\mathcal{L}_{24}$  constructed above, we obtain
		\begin{eqnarray*}
		%2C\cdot \mathcal{L} = 
	\sum\limits_{i=1}^{48} C \cdot l_i &\geq& 2\sum\limits_{p\in \text{Sing}(\mathcal{L})} \text{mult}_pC \\ 
		\Longrightarrow \sum\limits_{1}^{24} \mathcal{O}_X(1) \cdot C  &\geq& 2\sum\limits_{p\in \text{Sing}(\mathcal{L})} \text{mult}_pC \\ 
		\Longrightarrow 24 \text{deg}(C) &\geq& 2 \left(2\sum\limits_{p_i \in \text{Sing}_2(\mathcal{L})} \text{mult}_{p_i} C ~+~ 4\sum\limits_{p_j \in \text{Sing}_4(\mathcal{L})} \text{mult}_{p_j}C \right) \\
		\Longrightarrow 24 \text{deg}(C) &\geq& 4 \sum\limits_{p \in C\cap \text{Sing}(\mathcal{L})} \text{mult}_{p}C \\
		\Longrightarrow 6 \text{deg}(C) &\geq&  \sum\limits_{p \in C\cap \text{Sing}(\mathcal{L})} \text{mult}_{p}C.
		\end{eqnarray*}
		\fi

		%%%

		Here $\text{Sing}_2(\mathcal{L})$ and $\text{Sing}_4(\mathcal{L})$ denote the set of double points and the set of quadruple points of the arrangement $\mathcal{L}$, respectively. Therefore we get 
		\[
		\frac{\mathcal{O}_X(1) \cdot C}{\sum\limits_{p \in \text{Sing}(\mathcal{L})} \text{mult}_{p}C} = \frac{\text{deg}(C)}{ \sum\limits_{p \in\text{Sing}(\mathcal{L})} \text{mult}_{p}C} \geq \frac{1}{6} > \frac{1}{10}.
		\]
		This completes the proof of the claim.

	\end{example}

	\bibliographystyle{plain}
	\begin{thebibliography}{100}
	\bibitem{B} T. Bauer, Seshadri constants on algebraic surfaces, Math. Ann. \textbf{313} (1999), no.3, 547--583.
	\bibitem{CV} E. Carlini, A. Van Tuyl, Star configuration points and generic plane curves, Proc. Amer. Math. Soc. \textbf{139} (2011), no.12, 4181--4192.
	\bibitem{E} S. Eterovi\'c, Logarithmic Chern slopes of arrangements of rational sections in Hirzebruch surfaces,
		Master Thesis, Pontificia Universidad Cat\'olica de Chile, Santiago 2015.
		\bibitem{GHM} A. V. Geramita, B. Harbourne, J. Migliore, Star configurations in $\mathbb{P}^n$, J. Algebra, \textbf{376} (2013), 279--299.
		\bibitem{HM} K. Hanumanthu, A. Mukhopadhyay, {\it Multi-point Seshadri constants on ruled surfaces}, Proc. Amer. Math. Soc. \textbf{145} (2017), no. 12, 5145--5155.
		\bibitem{HS} K. Hanumanthu, A. Subramaniam, Bounded negativity and Harbourne constants on ruled surfaces, Manuscripta Math. \textbf{164} (2021) 431--454. 
		\bibitem{HR} B. Harbourne, J. Ro\'e,
Discrete behavior of Seshadri constants on surfaces, J. Pure Appl. Algebra \textbf{212} (2008), no.3, 616--627.
		\bibitem{Har} R. Hartshorne, {\it Algebraic geometry},
		Springer-Verlag, New York, 1977.
%		\bibitem{HD} D. Huybrechts, (2016). {\it Lectures on K3 Surfaces (Cambridge Studies in Advanced Mathematics)}. Cambridge: Cambridge University Press. doi:10.1017/CBO9781316594193
		\bibitem{JP}M. Janasz and P. Pokora, On Seshadri constants and point-curve configurations, Electron. Res. Arch., \textbf{28(2)} (2020)  795--805.

		%\bibitem{LP} R. Laface and P. Pokora, Towards the weighted bounded negativity conjecture
		%for blow-ups of algebraic surfaces, Manuscripta Math. \textbf{163} (2020), no. 3-4,
		%361--373.

			\bibitem{LP1} R. Laface and P. Pokora, 
		Local negativity of surfaces with non-negative Kodaira dimension and transversal configurations of curves, 
Glasg. Math. J. \textbf{62} (2020), no.1, 123--135.	
%		\bibitem{Mo} T. K.  Moe, On the number of cusps on cuspidal curves on Hirzebruch surfaces. Math. Nachr. 288(1), 76–88 (2015).
%		\bibitem{Mar} G. Martens, The gonality of curves on a Hirzebruch surface, Arch. Math. 67 (1996), 349–352.
		\bibitem{Nag} M. Nagata, On the 14-th problem of Hilbert, Am. J. Math. \textbf{81} (1959), 766--772.
\bibitem{Pok1}	P. Pokora, Harbourne constants and arrangements of lines on smooth hypersurfaces in
$\mathbb{P}_{\mathbb{C}}^3$,  Taiwanese J. Math., \textbf{20}, No. 1 (2016), 25--31.

		\bibitem{Pok} P. Pokora, Seshadri constants and special configurations of points in the projective plane,
		Rocky Mountain J. Math. \textbf{49(3)} (2019) 963 -- 978.
		\bibitem{PRS} P. Pokora, X. Roulleau and T. Szemberg, Bounded negativity, Harbourne constants and transversal
		arrangements of curves, Ann. Inst. Fourier (Grenoble) \textbf{67} (2017), no. 6, 2719–2735.
		\bibitem{PR} P. K. Roy,
Some results on Seshadri constants on surfaces of general type,  Eur. J. Math. \textbf{6} (2020), no.4, 1176--1190.
		\bibitem{RR} J. Ro\'e, J. Ross, 
An inequality between multipoint Seshadri constants, Geom. Dedicata \textbf{140} (2009), 175--181.
		\bibitem{SS} W. Syzdek, T. Szemberg, Seshadri fibrations of algebraic surfaces, Math. Nachr. \textbf{283} (2010),
no. 6, 902--908.
\bibitem{U} G. A. Urz\'ua,  Arrangements of curves and algebraic surfaces,  Thesis (Ph.D.) University of
Michigan, 2008, 166 pages.
	\end{thebibliography}

\end{document}

### 2024-03-16 Response to reviewer.tex
Added 'Response to reviewer

\documentclass[12pt,twoside,reqno]{amsart}
%\documentclass[12pt]{article}

\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{amsthm, amsmath, amscd, amssymb,centernot}
\usepackage[all]{xy}
\usepackage[T1]{fontenc}
\usepackage[left=2.5cm,top=2.5cm,bottom=3cm,right=2.5cm]{geometry}
\usepackage{amsthm, amsmath, amscd, amssymb,centernot}
\usepackage{comment}
\setlength{\headheight}{15.2pt}
\setlength\parskip{.1in}
\setlength\parindent{0.2in}

%\usepackage{tikz}https://www.overleaf.com/project/642e283246ec4730b8bdf398
\usepackage{csquotes}

\newcommand{\s}{\varepsilon}

\numberwithin{equation}{section}
\newtheorem{theorem}{Theorem}[section]
\newtheorem*{theorem*}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{definition}
\newtheorem{question}[theorem]{Question}

\begin{document}
\title{Response to Reviewer}
\begin{description}
\item [Mauscript Number] IJM-D-22-00005 \\
\item [Full Title] Seshadri constants on some blow ups of Projective spaces
\end{description}

We start by thanking the anonymous referee for carefully reading the manuscript and suggesting 
useful changes and also for pointing out an error in the definition of ``\textit{multiplicity of a curve along a line in $\mathbb{P}^3$}''. We hope that after making these changes, the paper has becomes more accessible for the readers and its overall quality has improved considerably. We have made all the changes suggested by the referee and some other modifications, which we felt necessary. Following are the detailed (point by point) explanation of changes that we have made on the basis of the report. \\

We agree with the referee about the problem in our way of using the definition of multiplicity of an irreducible curve $C$ along a line $l$, both 
contained in $\mathbb{P}^3$. We have made it clear in the manuscript now that this is defined as the length of zero dimensional 
scheme $C \cap l \subset \mathbb{P}^3$, as pointed out by the referee. On the basis of this new (correct) definition, we have modified our arguments in theorems of Section $4$ and that of Section $5$. We now get some restricted results about Seshadri constants in case of $r=5,6$ line blow ups of $\mathbb{P}^3$ (Proposition 4.3), $r=4,5,6$ and $7$ line blow ups of $\mathbb{P}^4$ (Proposition 5.4) and $r=3,4$ and $5$ line blow ups of $\mathbb{P}^5$ (Remark 4).  In the cases not covered in the above list, we get bounds mainly. We give precise values of Seshadri constants only when points are special, for example (2), (3) and (4) of Theorem 4.2, (2), (3) of Theorem 5.3, and (2) of Theorem 5.5. However we do compute $\varepsilon(X_{r,0}^k,L)$ in various cases which appear in Remarks 1,2, and 5 and are explained towards the end of this letter.\\

\textbf{List of minor mathematical issues we fixed:}
\begin{enumerate}
 \item We have changed the arguments in page 3, line -2, as per referee's suggestions.  
 \item We have mentioned now in line -9 of page 4 that we use (2) to conclude the result. 
 \item We have set $m_i = 0$ for $i = s+1,..., 2n$ and moved $m_i + m_{i+n}$ after the summation on page 5, line 1-2. 
 \item We deleted the second $\sum\limits_{i=1}^s$ in the repetition. 
 \item We have added the missing case in the proof of Theorem 3.3 on page 5, line 12. 
 \item On page 6 line -2, we have added a precise reference namely ``\textit{from inequality (3) of Theorem 3.3}''. 
 \item We replaced $d>0$ with $d \geq 0$ in the statements of Theorem 4.1 (1), (2), (3) and also in the proof. 
 \item We replaced $d>0$ with $d \geq 0$ in the statements of Theorem 5.1 (1), (2), (3), Proposition 5.2 and also in the proofs. 
\end{enumerate}

\textbf{List of grammar issues/typos we fixed:}
\begin{enumerate}
 \item Rectified the spelling mistake in Demailly. 
 \item ``One of the very important'' has been changed to ``One of the most important'' page 1, line -11.
 \item We changed ``Seshadri constant can be'' to ``Seshadri constants can be'' on page 1, line -6.
 \item Done.
 \item We replaced the phrase ``d is large enough as in Proposition 3.2'' with ``d is large enough namely 
 $\sum_{i=1}^s m_i - nd \leq b_l$, where $b_l$ is as in Proposition 3.2''.
 \item We changed the notation $H_2$ by $H'$ on page 6, line -9. 
 \item Done.
 \item Does not exist in the modified version.
 \item Does not exist in the modified version.
 \item Does not exist in the modified version.
\end{enumerate}

\textbf{Some other small changes which we have done:} \\
Second part of the paper is rewritten to some extent. We give here the detailed account of changes that we have done from the previous version.
\begin{enumerate}
    \item We introduce some notations in the beginning of \textit{Section 4}, which we use in the proof of Theorem 4.2 and in later part of the paper. We have also added a paragraph before Theorem 4.2 where we explain ``the meaning of multiplicity of $C$ along a line $l$''. 
    \item After Theorem 4.2, we have added a \textit{Remark 1} where we compute $\varepsilon(X_{r,0}^3,L)$ for $r=1,...,4$.
    \item We then added a Proposition 4.3 giving some partial results about $\varepsilon(X_{r,0}^3,L)$ for $r=5$ and 
    a \textit{Remark 2} bounding $\varepsilon(X_{5,0}^3,L)$. We leave $r=6,7$ cases as the results in those cases are similar to Prop. 4.3 and Rem. 2.
    \item In section 5, we have added a paragraph before Theorem 5.3, where we introduce some notation about the intersection of joins of lines $J(l_i, l_j)$ and of $J(l_i, l_k)$.
    \item After Theorem 5.3, we added a \textit{Remark 3}, where we compute $\varepsilon(X_{4,0}^4,L,x)$ when $x \in l_j \cap J(l_i,l_k)$.
    \item We then added a Propostion 5.4, where we get partial result about $\varepsilon(X_{4,0}^4,L)$ (we again leave $r=5,6,7$ cases).
    \item We also note in \textit{Remark 4}, that similar results like Prop. 5.4 holds for $\varepsilon(X_{r,0}^5,L)$ 
    for $r=3,4,$ and $5$ (note that for $r=1,2$ we have Theorem 5.5).
    \item Finally in \textit{Remark 5}, we have added a note about the global Seshadri constant $\varepsilon(X_{r,0}^k,L)$ for $k=4,5$ and $r=1,...,7$, $r=1,...,5$ respectively.
\end{enumerate}

\end{document}

### 2024-03-16 Response/Response to reviewer.tex
Praveen-16-March-24
Response to reviewer-By Praveen

--- 2024-03-16 Response to reviewer.tex
@@
 \begin{description}
-\item [Mauscript Number] IJM-D-22-00005 \\
-\item [Full Title] Seshadri constants on some blow ups of Projective spaces
+\item [Mauscript Number] GMJ 231005 \\
+\item [Full Title] Seshadri Constants of Curve Configurations on Surfaces
+\item [Author] Krishna Hanumanthu, Praveen Roy and Aditya Subramaniam
 \end{description}
@@
 We start by thanking the anonymous referee for carefully reading the manuscript and suggesting 
-useful changes and also for pointing out an error in the definition of ``\textit{multiplicity of a curve along a line in $\mathbb{P}^3$}''.
-We hope that after making these changes, the paper has becomes more accessible for the readers and its overall quality has improved considerably.
-We have made all the changes suggested by the referee and some other modifications, which we felt necessary.
+useful changes and also for pointing out an error in the Assumption 2.1 and therefore the ambiguity in Theorem 2.5. We also agree with the reviewer that the example 2.21 is 
+better to be shorten focusing only on the computation related to Seshadri constants.
+We have made all these changes, and we hope that after making these changes, the paper has becomes more accessible for the readers and its overall quality has improved considerably.
 Following are the detailed (point by point) explanation of changes that we have made on the basis of the report.
@@
 
-We agree with the referee about the problem in our way of using the definition of multiplicity of an irreducible curve $C$ along a line $l$, both 
-contained in $\mathbb{P}^3$. We have made it clear in the manuscript now that this is defined as the length of zero dimensional 
-scheme $C \cap l \subset \mathbb{P}^3$, as pointed out by the referee.
-On the basis of this new (correct) definition, we have modified our arguments in theorems of Section $4$ and that of Section $5$.
-We now get some restricted results about Seshadri constants in case of $r=5,6$ line blow ups of $\mathbb{P}^3$ (Proposition 4.3), $r=4,5,6$ and $7$ line blow ups of $\mathbb{P}^4$ (Proposition 5.4) and $r=3,4$ and $5$ line blow ups of $\mathbb{P}^5$ (Remark 4).
-In the cases not covered in the above list, we get bounds mainly.
-We give precise values of Seshadri constants only when points are special, for example (2), (3) and (4) of Theorem 4.2, (2), (3) of Theorem 5.3, and (2) of Theorem 5.5.
-However we do compute $\varepsilon(X_{r,0}^k,L)$ in various cases which appear in Remarks 1,2, and 5 and are explained towards the end of this letter.\\
+We agree with the referee about the problem in our way of using the Assumption 2.1. While writing the paper, we always had in mind the \textbf{connectedness of the arrangement}, 
+which we somehow missed to incorporate in the Assumption 2.1.
+We have made it clear in the manuscript now.
+Note that, now we don't require the semi-ampleness of divisor $A$ for $C_i^2$ to be positive, and it follows
+from the connectedness of the arrangement.
+Also, we would like to keep second assumption in Assumption 2.1, as removing that requires lot of new work and we aren't quite interested to carry out the required work, in that direction,
+as of now. The last concern of reviewer has also been addressed, we 
+have updated the last example 2.21 and it has been shorten. \\
 
-\textbf{List of minor mathematical issues we fixed:}
-\begin{enumerate}
- \item We have changed the arguments in page 3, line -2, as per referee's suggestions.  
- \item We have mentioned now in line -9 of page 4 that we use (2) to conclude the result. 
- \item We have set $m_i = 0$ for $i = s+1,..., 2n$ and moved $m_i + m_{i+n}$ after the summation on page 5, line 1-2. 
- \item We deleted the second $\sum\limits_{i=1}^s$ in the repetition. 
- \item We have added the missing case in the proof of Theorem 3.3 on page 5, line 12. 
- \item On page 6 line -2, we have added a precise reference namely ``\textit{from inequality (3) of Theorem 3.3}''. 
- \item We replaced $d>0$ with $d \geq 0$ in the statements of Theorem 4.1 (1), (2), (3) and also in the proof. 
- \item We replaced $d>0$ with $d \geq 0$ in the statements of Theorem 5.1 (1), (2), (3), Proposition 5.2 and also in the proofs. 
-\end{enumerate}
-
-\textbf{List of grammar issues/typos we fixed:}
-\begin{enumerate}
- \item Rectified the spelling mistake in Demailly. 
- \item ``One of the very important'' has been changed to ``One of the most important'' page 1, line -11.
- \item We changed ``Seshadri constant can be'' to ``Seshadri constants can be'' on page 1, line -6.
- \item Done.
- \item We replaced the phrase ``d is large enough as in Proposition 3.2'' with ``d is large enough namely 
- $\sum_{i=1}^s m_i - nd \leq b_l$, where $b_l$ is as in Proposition 3.2''.
- \item We changed the notation $H_2$ by $H'$ on page 6, line -9. 
- \item Done.
- \item Does not exist in the modified version.
- \item Does not exist in the modified version.
- \item Does not exist in the modified version.
-\end{enumerate}
-
-\textbf{Some other small changes which we have done:} \\
-Second part of the paper is rewritten to some extent. We give here the detailed account of changes that we have done from the previous version.
-\begin{enumerate}
-    \item We introduce some notations in the beginning of \textit{Section 4}, which we use in the proof of Theorem 4.2 and in later part of the paper.
-We have also added a paragraph before Theorem 4.2 where we explain ``the meaning of multiplicity of $C$ along a line $l$''.
-    \item After Theorem 4.2, we have added a \textit{Remark 1} where we compute $\varepsilon(X_{r,0}^3,L)$ for $r=1,...,4$.
-    \item We then added a Proposition 4.3 giving some partial results about $\varepsilon(X_{r,0}^3,L)$ for $r=5$ and 
-    a \textit{Remark 2} bounding $\varepsilon(X_{5,0}^3,L)$. We leave $r=6,7$ cases as the results in those cases are similar to Prop. 4.3 and Rem. 2.
-    \item In section 5, we have added a paragraph before Theorem 5.3, where we introduce some notation about the intersection of joins of lines $J(l_i, l_j)$ and of $J(l_i, l_k)$.
-    \item After Theorem 5.3, we added a \textit{Remark 3}, where we compute $\varepsilon(X_{4,0}^4,L,x)$ when $x \in l_j \cap J(l_i,l_k)$.
-    \item We then added a Propostion 5.4, where we get partial result about $\varepsilon(X_{4,0}^4,L)$ (we again leave $r=5,6,7$ cases).
-    \item We also note in \textit{Remark 4}, that similar results like Prop. 5.4 holds for $\varepsilon(X_{r,0}^5,L)$ 
-    for $r=3,4,$ and $5$ (note that for $r=1,2$ we have Theorem 5.5).
-    \item Finally in \textit{Remark 5}, we have added a note about the global Seshadri constant $\varepsilon(X_{r,0}^k,L)$ for $k=4,5$ and $r=1,...,7$, $r=1,...,5$ respectively.
-\end{enumerate}
+We once again thank the referee for a quick review, we hope that we addressed all the concern of the referee regarding this manuscript.
 

### 2024-03-16 Response/Response to reviewer.tex
Modified response-16-March

@@
 We start by thanking the anonymous referee for carefully reading the manuscript and suggesting 
-useful changes and also for pointing out an error in the Assumption 2.1 and therefore the ambiguity in Theorem 2.5. We also agree with the reviewer that the example 2.21 is 
+useful changes and also for pointing out an error in the Assumption 2.1 which lead to the ambiguity in Theorem 2.5. We also agree with the reviewer that the example 2.21 is 
 better to be shorten focusing only on the computation related to Seshadri constants.
 We have made all these changes, and we hope that after making these changes, the paper has becomes more accessible for the readers and its overall quality has improved considerably.
-Following are the detailed (point by point) explanation of changes that we have made on the basis of the report.
+Following are somewhat detailed explanation of changes that we have made on the basis of the report.
 \\
@@
 from the connectedness of the arrangement.
-Also, we would like to keep second assumption in Assumption 2.1, as removing that requires lot of new work and we aren't quite interested to carry out the required work, in that direction,
-as of now. The last concern of reviewer has also been addressed, we 
-have updated the last example 2.21 and it has been shorten. \\
+Additionally, we would prefer to retain the second part of Assumption 2.1, as removing that requires significant amount of additional work which we are currently not inclined to pursue.
+ Regarding the reviewer's final concern, we have revised Example 2.21, shortening it to focus solely on the computation of the Seshadri constant. \\
 

### 2024-03-16 sc-curve-config.tex
Actual version submitted
Aditya informed that the previous version was not the one we submitted and this is the one.

@@
 
-\address{Indian Institute of Science Education and Research Tirupati, Rami Reddy Nagar, Karakambadi Road, Mangalam (P.O.)
+\address{Indian Institute of Science Education and Research Tirupati, Rami Reddy Nagar, Karakambadi Road, Mangalam (P.O.),
 Tirupati, Andhra Pradesh, INDIA – 517507.}
@@
 \email{adityasubramaniam@labs.iisertirupati.ac.in}
-\subjclass[2020]{14C20,14N10, 14N20}
+\subjclass[2020]{14C20,14N10,14N20}
 
@@
 		\label{coro:star}
-		If $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ is a star configuration with $d \geq 4$  and $L$ is an ample line bundle on $X$ such that $ C_i \in |mL|$ for all $i$ and a positive integer $m>0$, then 
+		If $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ is a star configuration on a nonsingular projective surface $X$ with $d \geq 4$  and $L$ is an ample line bundle  on $X$ such that $ C_i \in |mL|$ for all $i$ and a positive integer $m>0$, then
 		$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \frac{1}{m(d-1)}.$$
@@
 		$$	\varepsilon_{\mathcal{C}_n'}(L)= \frac{3n(L\cdot C_1)}{f_1}= \frac{e+1}{e(n+1)}.$$
-		Thus in this case, both these constants agree.
+		Thus, in this case, both these constants agree.
 
@@
 		$$	\varepsilon_{\mathcal{K}'}(L)= \frac{21(L\cdot C_1)}{f_1}= \frac{e+1}{8e}.$$
-		Thus in this case too both these constants agree.
+		Thus, in this case too, both the constants agree.
 
@@
 		$$	\varepsilon_{\mathcal{W}'}(L)= \frac{45(L\cdot C_1)}{f_1}= \frac{e+1}{16e}.$$
-		Thus in this case too both the constants agree.
+		Thus, in this case too, both the constants agree.
 
@@
 
+\subsection*{Declaration of interests}
+The authors declare that they have no known competing financial interests or personal relationships
+that could have appeared to influence the work reported in this paper.
+
 	\bibliographystyle{plain}

### 2024-03-17 sc-curve-config.tex
Attempt 1-17th march-1:48 pm
Changes done by Praveen

@@
 \usepackage{xcolor}
+\usepackage{comment}
 
@@
 	\begin{assumption}\label{star1}
-		Let $\mathcal{C}=\{C_1,C_2, \ldots ,C_d\}$, $d\geq 4$ be a transversal arrangement of curves
+		Let $\mathcal{C}=\{C_1,C_2, \ldots ,C_d\}$, $d\geq 4$ be a \textcolor{red}{connected} transversal arrangement of curves
 		on a complex smooth projective surface $X$ with the following properties: 
@@
 
-		We describe the intersection behaviour of these lines 
-		below.
+		Now let $\mathcal{L} = \{l_1,l_2, \ldots,  l_{48}\}$ be the arrangement consisting of all these 48 lines. We fix two enumerations of the set 
+		$\{\zeta, -\zeta, i\zeta, -i\zeta \}$: $\alpha_1, \alpha_2, \alpha_3, \alpha_4$ and $\beta_1, \beta_2, \beta_3, \beta_4$ and then define 
+		\begin{eqnarray}
+		\mathcal{L}_{\alpha_i} := \text{Set of lines in } X \cap V(x_0 - \alpha_i x_1) \\
+		\mathcal{L}_{\beta_j} := \text{Set of lines in } X \cap V(x_2 - \beta_j x_3)
+		\end{eqnarray}
+Here $V(f)$ (for a polynomial $f$) denotes the vanishing locus of $f$.
+Note that, these $8$ sets, each consisting of $4$ lines of type $A$, has the property that each lines (of type $A$) appears in exactly two of these eight sets.
+Similarly, we can define
+$\mathcal{L}_{\alpha_i}'$, $\mathcal{L}_{\beta_j}'$ (lines of type $A'$)  and $\mathcal{L}_{\alpha_i}''$, $\mathcal{L}_{\beta_j} ''$ (lines of type $A''$) by intersecting $X$ with the 
+hyperplanes $V(x_0 - \alpha_i x_2)$, $V(x_1 - \beta_j x_3)$, and $V(x_0 - \alpha_i x_3)$, $V(x_1 - \beta_j x_2)$ respectively, and the same property holds as that of type $A$.
 
-		First, we consider intersections among lines of type A. 
-		If $$A_1: \; x_0 = \alpha x_1, \;  x_2 = \beta x_3 \text{ and } B_1: \; x_0 = \alpha' x_1, \; x_2 = \beta' x_3$$ then 
-		\[
-		A_1 \cap B_1 \neq \phi \Leftrightarrow x_1 = 0 \;  \text{or} \;  \alpha = \alpha' \; \text{and} \; x_3 = 0\;  \text{or} \; \beta = \beta'.
-		\]
-		This shows that a line $A_1$ of type $A$ meets three lines of the form  $x_0 = \alpha x_1,\; x_2 = \beta' x_3$ ($\beta' \in \{\zeta, -\zeta, i\zeta, -i\zeta \} \textbackslash \{\beta\}$) of type $A$ at $[\alpha :1 :0 :0]$ and 3 other lines of type $A$ of the form $x_0 = \alpha' x_1,\; x_2 = \beta x_3$ ($\alpha' \in \{\zeta, -\zeta, i\zeta, -i\zeta \} \textbackslash \{\alpha\}$) at $[0 :0 :\beta :1]$.
+This gives a collection of 24 sets which we rename as $\mathcal{L}_1$, $\mathcal{L}_2$, \ldots, $\mathcal{L}_{24}$  containing 4 lines each from $\mathcal{L}$ such that each $l_i$ is exactly in two of this list.
 
-		On the other hand, a line $A_1$ of type $A$ meets only 4 out of the 16 lines of type $A'$: 
-		\[
-		A_1 \cap \{x_0 = \alpha' x_2, x_1 = \beta' x_3\} \ne \emptyset
-		\]
-implies
-		%\begin{eqnarray*}
-			$x_0 = \alpha' x_2 = \alpha'  \beta x_3 \; \text{and} \; x_0 = \alpha x_1 = \alpha \beta' x_3$. This shows  
-			%\Rightarrow 
-			$\alpha'  \beta = \alpha \beta'$.
-Thus the choice of $\beta'$ determines $\alpha'$, giving 4 lines of type $A'$ .
-Moreover, the intersection point of $A_1$ and a line $\{x_0 = \alpha' x_2, x_1 = \beta' x_3\}$ of type $A'$
-			is given by $[\alpha \beta'  : \beta' : \beta : 1]$.
-
-			By a similar argument one can see that $A_1$ meets exactly 4 lines of type $A''$.
-
-		Now let $\mathcal{L} = \{l_1,l_2, \ldots,  l_{48}\}$ be the arrangement consisting of all the 48 lines of type $A$, $A'$ and $A''$ on $X$.
-
-		We claim that there exist 24 sets of lines 
-		$\mathcal{L}_1$, $\mathcal{L}_2$, \ldots , $\mathcal{L}_{24}$ containing 4 lines each from $\mathcal{L}$
-		satisfying the following conditions. Let $1 \le i \le 24$. 
-		\begin{itemize}
-		\item Each set $\mathcal{L}_i$ contains 4 lines of the same type. 
-		\item All the  four lines in each set $\mathcal{L}_i$ meet in one point. 
-		\item The divisor obtained by adding the four lines in each  $\mathcal{L}_i$ is linearly equivalent to $\mathcal{O}_X(1)$. 
-		\item Each $l_i$ is contained in exactly two of the sets  $\mathcal{L}_1$, $\mathcal{L}_2, \ldots, \mathcal{L}_{24}$. 
-	\end{itemize}	
-		We will prove that there are 8 sets of the above kind consisting of lines of type $A$. By a similar argument, we get the statement for types $A'$ and $A''$. 
-		%We will prove the 
-		%claim as well as the construction of $\mathcal{L}_1$, $\mathcal{L}_2$, \ldots, $\mathcal{L}_{24}$ simultaneously. 
-		Fix two enumerations of the set $\{\zeta, -\zeta, i\zeta, -i\zeta \}$: $\alpha_1, \alpha_2, \alpha_3, \alpha_4$ and 
-$\beta_1, \beta_2, \beta_3, \beta_4$.
-
-First, consider the line $$l_{\alpha_1,\beta_1} = \{x_0 = \alpha_1 x_1 \; \text{and} \; x_2 = \beta_1 x_3\}$$ of type $A$.
-From the intersection behaviour described above, we know that $l_{\alpha_1,\beta_1}$  meets exactly six lines of type $A$ which are given by:
-		\begin{eqnarray*} 
-		l_{\alpha_1,\beta_i}, &\text{ for }& i=2,3,4, \text{ and }\\
-		l_{\alpha_j,\beta_1}, &\text{ for } & j=2,3,4.
-		\end{eqnarray*}
-
-The four lines $l_{\alpha_1,\beta_1},l_{\alpha_1,\beta_2},l_{\alpha_1,\beta_3},l_{\alpha_1,\beta_4} $ meet at the point 
- $[\alpha_1 :1 :0 :0]$ and the four lines $l_{\alpha_1,\beta_1},l_{\alpha_2,\beta_1},l_{\alpha_3,\beta_1},l_{\alpha_4,\beta_1}$ meet at the point  $[0 :0 :\beta_1 :1]$.
-
- We define  
- \begin{eqnarray*} 
- \mathcal{L}_{\alpha_1} &=&\{l_{\alpha_1,\beta_1},l_{\alpha_1,\beta_2},l_{\alpha_1,\beta_3},l_{\alpha_1,\beta_4} \},\\ 
-\mathcal{L}_{\beta_1} &=& \{l_{\alpha_1,\beta_1},l_{\alpha_2,\beta_1},l_{\alpha_3,\beta_1},l_{\alpha_4,\beta_1} \}.
-\end{eqnarray*}
-
-Similarly, we define $\mathcal{L}_{\alpha_i}$ and  $\mathcal{L}_{\beta_j}$ for every 
-$2 \le i, j \le 4$.
-
-Note that every line of type $A$ appears in exactly two of the eight sets 
-$\mathcal{L}_{\alpha_i}$ and  $\mathcal{L}_{\beta_j}$, where $1\le i, j \le 4$. 
-More precisely,  a line $l_{\alpha_i,\beta_j}$ of type $A$ is contained only  in $\mathcal{L}_{\alpha_i}$ and in $ \mathcal{L}_{\beta_j}$.
-
-		%\[
-		%\bigcup\limits_{i=1}^{4} \mathcal{L}_{\alpha_i} = \text{Set of all lines of type $A$} = \bigcup\limits_{j=1}^{4} \mathcal{L}_{\beta_j}
-		%\]
-
-The collection of these $\mathcal{L}_{\alpha_i}$ and $\mathcal{L}_{\beta_j}$ contribute $8$ sets of lines of type $A$. 
-		Similarly we can define $\mathcal{L}_{\alpha_i}'$ and $\mathcal{L}_{\beta_j}'$ from type $A'$ and $\mathcal{L}_{\alpha_i}''$ and $\mathcal{L}_{\beta_j}''$ from type $A''$.
-This gives a collection of 24 sets which we rename
-		as $\mathcal{L}_1$, $\mathcal{L}_2$, \ldots, $\mathcal{L}_{24}$ such that each $l_i$ is exactly in two of this list.
-
-		We also note that all the lines in $\mathcal{L}_{\alpha_i}$ (respectively, in $\mathcal{L}_{\beta_j}$) lie
-		in the hyperplane given by the vanishing of $x_0 - \alpha_i x_1$ (respectively, $x_2 - \beta_j x_3$) in $\mathbb{P}^3$.
-In fact, the intersection of these hyperplanes with $X$ is precisely the four lines in question.
-		Therefore, for $1 \le i, j \le 4$, 
-		\begin{eqnarray*}
-		\mathcal{O}_X(1) &\sim&  \; l_{\alpha_i,\beta_1} + l_{\alpha_i,\beta_2} + l_{\alpha_i,\beta_3} + l_{\alpha_i,\beta_4}, \text{ and } \\
-		\mathcal{O}_X(1) &\sim& \;  l_{\alpha_1,\beta_j} + l_{\alpha_2,\beta_j} + l_{\alpha_3,\beta_j} + l_{\alpha_4,\beta_j}.
-		\end{eqnarray*}
-
-This proves our claim.
-
-		From the intersection behaviour described above, it is clear that the only singular points for the arrangement $\mathcal{L}$ are either double points or quadruple points; \cite[Example 3.3]{Pok1}.
+From the intersection behaviour which is well known, it is clear that the only singular points for the arrangement $\mathcal{L}$ are either double points or quadruple points; \cite[Example 3.3]{Pok1}.
 It is also not difficult to see that the number of singular points on any line  in $\mathcal{L}$ is 10, as we show now.
 		It suffices to verify this assertion for a line of type $A$.
-Given a line $l_{\alpha_i,\beta_j}$ of type $A$, we know that it has two quadruple points $[\alpha_i :1 :0 :0]$ and $[0 :0 :\beta_j :1]$.
+Given a line, denoted by $l_{\alpha_i,\beta_j}$ of type $A$, we know that it has two quadruple points $[\alpha_i :1 :0 :0]$ and $[0 :0 :\beta_j :1]$.
 We also know that each line of type $A$ meets

### 2024-03-17 sc-curve-config.tex
Attempt-2-17 March
Some more modification

@@
 		$\{\zeta, -\zeta, i\zeta, -i\zeta \}$: $\alpha_1, \alpha_2, \alpha_3, \alpha_4$ and $\beta_1, \beta_2, \beta_3, \beta_4$ and then define 
-		\begin{eqnarray}
+		\begin{eqnarray*}
 		\mathcal{L}_{\alpha_i} := \text{Set of lines in } X \cap V(x_0 - \alpha_i x_1) \\
 		\mathcal{L}_{\beta_j} := \text{Set of lines in } X \cap V(x_2 - \beta_j x_3)
-		\end{eqnarray}
-Here $V(f)$ (for a polynomial $f$) denotes the vanishing locus of $f$.
+		\end{eqnarray*}
+Here $V(f)$ (for a homogeneous polynomial $f$) denotes the vanishing locus of $f$.
 Note that, these $8$ sets, each consisting of $4$ lines of type $A$, has the property that each lines (of type $A$) appears in exactly two of these eight sets.
@@
 
-From the intersection behaviour which is well known, it is clear that the only singular points for the arrangement $\mathcal{L}$ are either double points or quadruple points; \cite[Example 3.3]{Pok1}.
+From the intersection behaviour of these lines, which is well known on Fermat quartic, it is clear that the only singular points for the arrangement $\mathcal{L}$ are either double points or quadruple points; \cite[Example 3.3]{Pok1}.
 It is also not difficult to see that the number of singular points on any line  in $\mathcal{L}$ is 10, as we show now.
@@
 		$$\varepsilon(X, \mathcal{O}_X(1), \text{Sing}(\mathcal{L})) \le \sqrt{\frac{4}{216}} \sim 0.136.$$
-
 In fact, we claim that
@@
 		\]
-
 Note that each line $l_{\alpha_i,\beta_j}$ has degree 1 in $\mathbb{P}^3$. So,  from the above discussion, it is clear that 

### 2024-03-17 sc-curve-config.tex
Attempt-3-17 March
Version after removing '24 sets of lines argument..'

@@
 		Let $X \subset \mathbb{P}^3$ be a Fermat quartic defined by the vanishing locus of $x_0^4 + x_1^4 + x_2^4 + x_3^4$, where $x_0, \ldots, x_3$ are the coordinates of $\mathbb{P}^3$. 
-Then $X$ contains the following 48 lines; 16 from each of the following three types:
+		Then $X$ contains the following 48 lines (denoted by $l_{\alpha, \beta}$); 16 from each of the following three types: 
 		\begin{eqnarray*}
@@
 		where $\alpha, \beta \in \{\zeta, -\zeta, i\zeta, -i\zeta \}$ and $\zeta$ is a primitive eighth root of unity.
+We fix two enumeration $\alpha_i, \beta_j$, for $1\leq i, j \leq 4$ of the set $\{\zeta, -\zeta, i\zeta, -i\zeta \}$.
 
-		Now let $\mathcal{L} = \{l_1,l_2, \ldots,  l_{48}\}$ be the arrangement consisting of all these 48 lines. We fix two enumerations of the set 
-		$\{\zeta, -\zeta, i\zeta, -i\zeta \}$: $\alpha_1, \alpha_2, \alpha_3, \alpha_4$ and $\beta_1, \beta_2, \beta_3, \beta_4$ and then define 
-		\begin{eqnarray*}
-		\mathcal{L}_{\alpha_i} := \text{Set of lines in } X \cap V(x_0 - \alpha_i x_1) \\
-		\mathcal{L}_{\beta_j} := \text{Set of lines in } X \cap V(x_2 - \beta_j x_3)
-		\end{eqnarray*}
-Here $V(f)$ (for a homogeneous polynomial $f$) denotes the vanishing locus of $f$.
-Note that, these $8$ sets, each consisting of $4$ lines of type $A$, has the property that each lines (of type $A$) appears in exactly two of these eight sets.
-Similarly, we can define
-$\mathcal{L}_{\alpha_i}'$, $\mathcal{L}_{\beta_j}'$ (lines of type $A'$)  and $\mathcal{L}_{\alpha_i}''$, $\mathcal{L}_{\beta_j} ''$ (lines of type $A''$) by intersecting $X$ with the 
-hyperplanes $V(x_0 - \alpha_i x_2)$, $V(x_1 - \beta_j x_3)$, and $V(x_0 - \alpha_i x_3)$, $V(x_1 - \beta_j x_2)$ respectively, and the same property holds as that of type $A$.
-
-This gives a collection of 24 sets which we rename as $\mathcal{L}_1$, $\mathcal{L}_2$, \ldots, $\mathcal{L}_{24}$  containing 4 lines each from $\mathcal{L}$ such that each $l_i$ is exactly in two of this list.
-
+Now let $\mathcal{L} = \{l_1,l_2, \ldots,  l_{48}\}$ be the arrangement consisting of all these 48 lines.
 From the intersection behaviour of these lines, which is well known on Fermat quartic, it is clear that the only singular points for the arrangement $\mathcal{L}$ are either double points or quadruple points; \cite[Example 3.3]{Pok1}.
@@
 		$\mathcal{L}$. By B\'ezout's theorem, we have the following inequality for every line $l \in \mathcal{L}$:
-		$$C \cdot l \ge \sum_{p \in l \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C.$$
-
-		We now sum such inequalities over all the 24 sets constructed above.
-Each such set contributes $C\cdot \mathcal{O}_X(1) = \text{deg}(C)$ to the left hand side.
-On the right hand side, each line appears twice.
-Since each double point appears in two lines and each quadruple point appears in four lines, we obtain
+		$$2 C \cdot l \ge 2\left( \sum_{p \in l \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right).$$
+We now sum such inequalities over all the 48 lines and then we re-group the lines (as a set of 4), in such a way that sum of each group corresponds to $\mathcal{O}_X(1)$.  Therefore, we get
+               \begin{eqnarray*}
+                \sum\limits_{i=1}^{48} 2 C \cdot l_i &\ge& \sum\limits_{i=1}^{48} 2\left( \sum_{p \in l_i \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right) \\
+                \Rightarrow  \sum\limits_{i=1}^{24} C \cdot \mathcal{O}_X(1) &\ge&  2\left( \sum\limits_{i=1}^{48}\sum_{p \in l_i \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right).
+               \end{eqnarray*}
+Now, since each double point appears in two lines and each quadruple point appears in four lines, we obtain 
 		\begin{eqnarray*}
@@
 		\end{eqnarray*}
-
 		%%%%%
@@
 		\fi
-
+		%
 		%%%
-
 Here $\text{Sing}_2(\mathcal{L})$ and $\text{Sing}_4(\mathcal{L})$ denote the set of double points and the set of quadruple points of the arrangement $\mathcal{L}$, respectively. Therefore we get 

### 2024-03-17 Response/Response to reviewer.tex
Modified-17th March
Added the changes in itemized form.

@@
 \\
+\begin{itemize}
+\item We agree with the referee about the problem in our way of using the Assumption 2.1. While writing the paper, we always had in mind the \textbf{connectedness of the arrangement}, 
+which we somehow missed to incorporate in the Assumption 2.1. We have now made it clear in the manuscript. \\
+\item Note that, now we don't require the semi-ampleness of divisor $A$ for $C_i^2$ to be positive, and it follows 
+from the connectedness of the arrangement. Additionally, we would prefer to retain the second part of Assumption 2.1, as removing that requires 
+significant amount of additional work which we are currently not inclined to pursue. In-fact even the statement of Theorem 2.5 will change, if we remove the second assumption. 
+By the phrase `curves are linearly equivalent to a fixed divisor $A$', we mean that, $C_i \in |A|$ (linear system of $A$) for all $i$. \\
+\item Regarding the reviewer's final concern, we have revised Example 2.21 considerably. We have now shortened it to focus solely on the computation of the Seshadri constant.
+\end{itemize}
 
-We agree with the referee about the problem in our way of using the Assumption 2.1. While writing the paper, we always had in mind the \textbf{connectedness of the arrangement}, 
-which we somehow missed to incorporate in the Assumption 2.1.
-We have made it clear in the manuscript now.
-Note that, now we don't require the semi-ampleness of divisor $A$ for $C_i^2$ to be positive, and it follows
-from the connectedness of the arrangement.
-Additionally, we would prefer to retain the second part of Assumption 2.1, as removing that requires significant amount of additional work which we are currently not inclined to pursue.
- Regarding the reviewer's final concern, we have revised Example 2.21, shortening it to focus solely on the computation of the Seshadri constant. \\
-
-We once again thank the referee for a quick review, we hope that we addressed all the concern of the referee regarding this manuscript.
+We once again thank the referee for a quick review, we hope that we addressed all the concerns of the referee regarding this manuscript.
 

### 2024-03-18 sc-curve-config.tex
Attempt-4 18th March
Made the example more clearer

@@
 Given a line, denoted by $l_{\alpha_i,\beta_j}$ of type $A$, we know that it has two quadruple points $[\alpha_i :1 :0 :0]$ and $[0 :0 :\beta_j :1]$.
-We also know that each line of type $A$ meets
+		In fact these points are intersection of lines in $\{l_{\alpha_i,\beta_j} \mid 1\leq j \leq 4 \} = X \cap V(x_0 - \alpha_i x_1)$ and in $\{l_{\alpha_i,\beta_j} \mid 1\leq i \leq 4 \} = X \cap V(x_2 - \beta_j x_3)$ respectively.
+		Note also that, sum of lines from any of these sets is linearly equivalent to $\mathcal{O}_X(1)$. We also know that each line of type $A$ meets 
 		4 lines each of type $A'$ and $A''$ and these points are all double points.

### 2024-03-18 Response/Response to reviewer.tex
Changes made by Krishna-18 March (3:35 PM)

--- 2024-03-16 Response/Response to reviewer.tex
@@
 \item [Mauscript Number] GMJ 231005 \\
-\item [Full Title] Seshadri Constants of Curve Configurations on Surfaces
-\item [Author] Krishna Hanumanthu, Praveen Roy and Aditya Subramaniam
+\item [Title] Seshadri Constants of Curve Configurations on Surfaces
+\item [Authors] Krishna Hanumanthu, Praveen Roy and Aditya Subramaniam
 \end{description}
 
-We start by thanking the anonymous referee for carefully reading the manuscript and suggesting 
-useful changes and also for pointing out an error in the Assumption 2.1 and therefore the ambiguity in Theorem 2.5. We also agree with the reviewer that the example 2.21 is 
-better to be shorten focusing only on the computation related to Seshadri constants.
-We have made all these changes, and we hope that after making these changes, the paper has becomes more accessible for the readers and its overall quality has improved considerably.
-Following are the detailed (point by point) explanation of changes that we have made on the basis of the report.
+We thank the referee for carefully reading the manuscript and suggesting 
+many useful changes and also for pointing out an error in the Assumption 2.1 which leads to 
+ambiguities at several places. We fixed this error by assuming that the arrangement is connected.
+
+We also agree with the referee that Example 2.21 can be shortened and it is better to 
+focus on the computation of Seshadri constants.
+
+Below we describe in detail the changes made to the manuscript based on the referee's comments. 
+%We have made all these changes, and we hope that after making these changes, the paper has becomes more accessible for the readers and its overall quality has improved considerably.
+Following are somewhat detailed explanation of changes that we have made on the basis of the report.
 \\
+\begin{itemize}
+\item Following the referee's suggestion, we included the assumption that the arrangement $\mathcal{C}$ is \textit{connected}.
+We added a remark immediately after Assumption 2.1 mentioning that the connectedness assumption implies that $C_i \cdot C_j > 0$ for all $i,j$.
 
-We agree with the referee about the problem in our way of using the Assumption 2.1. While writing the paper, we always had in mind the \textbf{connectedness of the arrangement}, 
-which we somehow missed to incorporate in the Assumption 2.1.
-We have made it clear in the manuscript now.
-Note that, now we don't require the semi-ampleness of divisor $A$ for $C_i^2$ to be positive, and it follows
-from the connectedness of the arrangement.
-Also, we would like to keep second assumption in Assumption 2.1, as removing that requires lot of new work and we aren't quite interested to carry out the required work, in that direction,
-as of now. The last concern of reviewer has also been addressed, we 
-have updated the last example 2.21 and it has been shorten. \\
+\item We also removed the unnecessary assumption that all the curves do not meet at any point. Referee correctly noted that this is not necessary for the main results.
 
-We once again thank the referee for a quick review, we hope that we addressed all the concern of the referee regarding this manuscript.
+We only needed this assumption while computing the configurational Seshadri constants in Section 2.3. We therefore added the required assumption at the beginning of Seciton 2.3.
+
+%agree with the referee about the problem in our way of using the Assumption 2.1. While writing the paper, we always had in mind the \textbf{connectedness of the arrangement}, 
+%which we somehow missed to incorporate in the Assumption 2.1. We have now made it clear in the manuscript. \\
+%\item Note that, now we don't require the semi-ampleness of divisor $A$ for $C_i^2$ to be positive, and it follows 
+%from the connectedness of the arrangement. 
+\item We retained the condition that all curves in our arrangements are linearly equivalent to a specific divisor.
+Many of the results and questions we state depend on this assumption.
+So removing this assumption will require a substantial re-working of the paper.
+
+%Additionally, we would prefer to retain the second part of Assumption 2.1, as removing that requires 
+%significant amount of additional work which we are currently not inclined to pursue. In-fact even the statement of Theorem 2.5 will change, if we remove the second assumption. 
+%By the phrase `curves are linearly equivalent to a fixed divisor $A$', we mean that, $C_i \in |A|$ (linear system of $A$) for all $i$. \\
+
+\item We have revised Example 2.21 considerably. We shortened it to focus solely on the computation of the Seshadri constant.
+\end{itemize}
+
+%We once again thank the referee for a quick review, we hope that we addressed all the concerns of the referee regarding this manuscript.
 

### 2024-03-18 sc-curve-config.tex
Changes made by Krishna-18 March (3:35 PM)

--- 2024-03-17 sc-curve-config.tex
@@
 	\begin{assumption}\label{star1}
-		Let $\mathcal{C}=\{C_1,C_2, \ldots ,C_d\}$, $d\geq 4$ be a \textcolor{red}{connected} transversal arrangement of curves
-		on a complex smooth projective surface $X$ with the following properties: 
-		\begin{itemize}
-			\item There is no point where all the curves meet, i.e., $t_d=0.$
-			\item  All the curves $C_i$ in $\mathcal{C}$ are linearly equivalent to a
+		Let $\mathcal{C}=\{C_1,C_2, \ldots ,C_d\}$, $d\geq 4$ be a connected 
+  transversal arrangement of curves 
+		on a complex smooth projective surface $X$ such that all the curves 
+  $C_i$ in $\mathcal{C}$ are linearly equivalent to a
 			fixed divisor $A$ on $X$.
-		\end{itemize}
+ % with the following properties: 
+%		\begin{itemize}
+%			\item There is no point where all the curves meet, i.e., $t_d=0.$
+%			\item  All the curves $C_i$ in $\mathcal{C}$ are linearly equivalent to a
+%			fixed divisor $A$ on $X$.
+%		\end{itemize}
 	\end{assumption}
 
+ \begin{remark} 
+Since each curve in $\mathcal{C}$ is assumed to be linearly equivalent to a fixed divisor $A$, the connectedness hypothesis in 
+Assumption \ref{star1} implies in particular that $C_i\cdot C_j > 0$ for all $1\le i,j \le d$.  Note that the connectedness hypothesis will follow if $A^2 > 0$. 
+ \end{remark}
 	\begin{definition}
@@
 \subsection{Lower bounds on configurational Seshadri constants}\label{bounds}
-We now give some lower bounds on configurational Seshadri constants on ruled surfaces and on surfaces of non-negative Kodaira dimension.
+We now give some lower bounds on configurational Seshadri constants on ruled surfaces and on surfaces of non-negative Kodaira dimension.	We will 
+work with arrangements of curves satisfying Assumption \ref{star1}. Further, we assume that 
+there is no point where all the curves in $\mathcal{C}$ meet, i.e., $t_d=0.$
 
@@
 		$\mathcal{C}$ is numerically equivalent to $A=aC_0+bf$ with $a > 0$
-		and $b \ge ae$.
-Assume further that either $a\geq 2$ or if $a=1$, there exists a subset of four curves in $\mathcal{C}$ such that there is no point common to all the four curves.
+		and $b \ge ae$. Assume further that all the curves in $\mathcal{C}$ do not meet in a point and that 
+  either $a\geq 2$ or if $a=1$, there exists a subset of four curves in $\mathcal{C}$ such that there is no point common to all the four curves.
 Then we have the following Hirzebruch-type inequality for $\mathcal{C}$:\\
@@
 		Let $X$ be a smooth complex projective surface with non-negative Kodaira dimension and let $C=C_1 + \cdots + C_d$ be a transversal configuration of smooth curves satisfying Assumption \ref{star1}.
-Let $L$ be an ample line bundle on $X$.
-Then
+Assume further that all the curves in $\mathcal{C}$ do not meet in a point.
+  Let $L$ be an ample line bundle on $X$. Then
 		$$\varepsilon_{\mathcal{C}}(
@@
 		Let $X \subset \mathbb{P}^3$ be a Fermat quartic defined by the vanishing locus of $x_0^4 + x_1^4 + x_2^4 + x_3^4$, where $x_0, \ldots, x_3$ are the coordinates of $\mathbb{P}^3$. 
-		Then $X$ contains the following 48 lines (denoted by $l_{\alpha, \beta}$); 16 from each of the following three types: 
+		Then $X$ contains the following 48 lines; 
+  %(denoted by $l_{\alpha, \beta}$); 
+  16 from each of the following three types: 
 		\begin{eqnarray*}
@@
 		where $\alpha, \beta \in \{\zeta, -\zeta, i\zeta, -i\zeta \}$ and $\zeta$ is a primitive eighth root of unity.
-We fix two enumeration $\alpha_i, \beta_j$, for $1\leq i, j \leq 4$ of the set $\{\zeta, -\zeta, i\zeta, -i\zeta \}$.
+We fix two enumerations $\alpha_i, \beta_j$, for $1\leq i, j \leq 4$ of the set $\{\zeta, -\zeta, i\zeta, -i\zeta \}$.
 
 Now let $\mathcal{L} = \{l_1,l_2, \ldots,  l_{48}\}$ be the arrangement consisting of all these 48 lines. 
-From the intersection behaviour of these lines, which is well known on Fermat quartic, it is clear that the only singular points for the arrangement $\mathcal{L}$ are either double points or quadruple points; \cite[Example 3.3]{Pok1}.
-It is also not difficult to see that the number of singular points on any line  in $\mathcal{L}$ is 10, as we show now.
+Intersection behaviour of lines on a Fermat quartic is classically well-known. 
+%From the intersection behaviour of these lines, which is well known on Fermat quartic, 
+In particular, it is known that the only singular points for the arrangement $\mathcal{L}$ are either double points or quadruple points; \cite[Example 3.3]{Pok1}.
+It is also not difficult to see that the number of singular points on any line $l$ in $\mathcal{L}$ is 10.
+Of these, two are quadruple points obtained by intersecting $l$ with lines of the same type.
+The remaining eight points are double points obtained by intersecting $l$ with lines of different types.
+
+{\color{red} Can we remove the following paragraph?}
+
+For the convenience of the reader, we quickly recall the argument below.  
 		It suffices to verify this assertion for a line of type $A$.
 Given a line, denoted by $l_{\alpha_i,\beta_j}$ of type $A$, we know that it has two quadruple points $[\alpha_i :1 :0 :0]$ and $[0 :0 :\beta_j :1]$.
-We also know that each line of type $A$ meets
+		In fact, these points are obtained by intersecting the lines in $\{l_{\alpha_i,\beta_j} \mid 1\leq j \leq 4 \} = X \cap V(x_0 - \alpha_i x_1)$ with those in  $\{l_{\alpha_i,\beta_j} \mid 1\leq i \leq 4 \} = X \cap V(x_2 - \beta_j x_3)$.
+		Note also that the sum of lines from any one of these sets is linearly equivalent to $\mathcal{O}_X(1)$. We also know that each line of type $A$ meets 
 		4 lines each of type $A'$ and $A''$ and these points are all double points.
 Therefore in all there are 10 singular points on a line of type $A$.
-By a similar argument one can show this for lines of type $A'$ and type $A''$ also.
+By a similar argument one can show this for lines of type $A'$ and type $A''$.
 
@@
 		$$2 C \cdot l \ge 2\left( \sum_{p \in l \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right).$$
-We now sum such inequalities over all the 48 lines and then we re-group the lines (as a set of 4), in such a way that sum of each group corresponds to $\mathcal{O}_X(1)$.  Therefore, we get
+
+We now sum such inequalities over all the 48 lines and then group the lines into sets of four lines, in such a way that the sum of each group corresponds to $\mathcal{O}_X(1)$.  Therefore we get
                \begin{eqnarray*}
@@
                \end{eqnarray*}
-Now, since each double point appears in two lines and each quadruple point appears in four lines, we obtain 
+
+Since each double point appears in two lines and each quadruple point appears in four lines, we obtain 
 		\begin{eqnarray*}
@@
 		%%%
+
 Here $\text{Sing}_2(\mathcal{L})$ and $\text{Sing}_4(\mathcal{L})$ denote the set of double points and the set of quadruple points of the arrangement $\mathcal{L}$, respectively. Therefore we get 
@@
 	\end{example}
+
+ \subsection*{Acknowledgements} We thank the referee for a careful reading of the paper and for giving many corrections and useful comments which substantially improved the paper.
+The first author is partially supported by a grant from Infosys Foundation.
 

### 2024-03-18 sc-curve-config.tex
Changes by Krishna-18 March (6:00PM)

@@
 		where $\alpha, \beta \in \{\zeta, -\zeta, i\zeta, -i\zeta \}$ and $\zeta$ is a primitive eighth root of unity.
-We fix two enumerations $\alpha_i, \beta_j$, for $1\leq i, j \leq 4$ of the set $\{\zeta, -\zeta, i\zeta, -i\zeta \}$.
+%We fix two enumerations $\alpha_i, \beta_j$, for $1\leq i, j \leq 4$ of the set $\{\zeta, -\zeta, i\zeta, -i\zeta \}$.
 
@@
 
-{\color{red} Can we remove the following paragraph?}
+For a fixed $\alpha \in \{\zeta, -\zeta, i\zeta, -i\zeta \}$, the hyperplane section $X \cap V(x_0 - \alpha x_1)$ is the union of the four lines of type $A$ in $\mathcal{L}$ 
+given by  
+$x_0 = \alpha x_1 \; \text{and} \; x_2 = \beta_j x_3$
+for  $1\leq j \leq 4$.
+Consequiently, the sum of these four lines is linearly equivalent to $\mathcal{O}_X(1)$.
+The 48 lines in $\mathcal{L}$ can be partitioned into sets of 4 lines each such that the sum of the four lines in each set is
+linearly equivalent to $\mathcal{O}_X(1)$.
 
-For the convenience of the reader, we quickly recall the argument below.  
-		It suffices to verify this assertion for a line of type $A$.
+%{\color{red} Can we remove the following paragraph?}
+
+%For the convenience of the reader, we quickly recall the argument %below.  
+%		It suffices to verify this assertion for a line of type $A$.
 Given a line, denoted by $l_{\alpha_i,\beta_j}$ of type $A$, we know that it has two quadruple points $[\alpha_i :1 :0 :0]$ and $[0 :0 :\beta_j :1]$.
-		In fact, these points are obtained by intersecting the lines in $\{l_{\alpha_i,\beta_j} \mid 1\leq j \leq 4 \} = X \cap V(x_0 - \alpha_i x_1)$ with those in  $\{l_{\alpha_i,\beta_j} \mid 1\leq i \leq 4 \} = X \cap V(x_2 - \beta_j x_3)$.
-		Note also that the sum of lines from any one of these sets is linearly equivalent to $\mathcal{O}_X(1)$. We also know that each line of type $A$ meets 
-		4 lines each of type $A'$ and $A''$ and these points are all double points.
+%		In fact, these points are obtained by intersecting the lines in $\{l_{\alpha_i,\beta_j} \mid 1\leq j \leq 4 \} = X \cap V(x_0 - \alpha_i x_1)$ with those in  $\{l_{\alpha_i,\beta_j} \mid 1\leq i \leq 4 \} = X \cap V(x_2 - \beta_j x_3)$.
+%		Note also that the sum of lines from any one of these sets is linearly equivalent to $\mathcal{O}_X(1)$. We also know that each line of type $A$ meets 
+%		4 lines each of type $A'$ and $A''$ and these points are all double points.
 Therefore in all there are 10 singular points on a line of type $A$.

### 2024-03-18 sc-curve-config.tex
Changes by Krishna-18th March (8:35)

@@
 
-\address{UM-DAE Centre for Excellence in Basic Sciences
-"Nalanda", Opp Nano Sciences Building,
-University of Mumbai, Vidyanagari,
-Mumbai 400098, India.}
+\address{UM-DAE Centre for Excellence in Basic Sciences, University of Mumbai Santacruz, Mumbai 400098, India}
 
@@
 
-For a fixed $\alpha \in \{\zeta, -\zeta, i\zeta, -i\zeta \}$, the hyperplane section $X \cap V(x_0 - \alpha x_1)$ is the union of the four lines of type $A$ in $\mathcal{L}$ 
+%For a fixed $\alpha \in \{\zeta, -\zeta, i\zeta, -i\zeta \}$,
+
+The hyperplane section $X \cap V(x_0 - \zeta x_1)$ is the union of the four lines of type $A$ in $\mathcal{L}$ 
 given by  
-$x_0 = \alpha x_1 \; \text{and} \; x_2 = \beta_j x_3$
-for  $1\leq j \leq 4$.
-Consequiently, the sum of these four lines is linearly equivalent to $\mathcal{O}_X(1)$.
-The 48 lines in $\mathcal{L}$ can be partitioned into sets of 4 lines each such that the sum of the four lines in each set is
-linearly equivalent to $\mathcal{O}_X(1)$.
+$x_0 = \zeta x_1 \; \text{and} \; x_2 = \beta_j x_3$
+for  $1\leq j \leq 4$. Consequently, the sum of these four lines is linearly equivalent to $\mathcal{O}_X(1)$. Similarly, the sum of the four lines 
+$x_0 = \alpha_i x_1 \; \text{and} \; x_2 = \zeta x_3$ is linearly equivalent to $\mathcal{O}_X(1)$. Thus we note that the line 
+$x_0 = \zeta x_1 \; \text{and} \; x_2 = \zeta x_3$ is in two different sets of 4 lines each so that the sum of lines in each set is linearly equivalent to $\mathcal{O}_X(1)$.
+Using a similar argument, one can see that there are 24 sets of 4 lines each such that each line in $\mathcal{L}$ appears in \textit{exactly} two of the sets and the sum of the 4 lines in each set is linearly equivalent to $\mathcal{O}_X(1)$.
+
+%The 48 lines in $\mathcal{L}$ can be partitioned into sets of 4 lines each such that the sum of the four lines in each set is  linearly equivalent to $\mathcal{O}_X(1)$.
 
@@
 		\]
-Note that each line $l_{\alpha_i,\beta_j}$ has degree 1 in $\mathbb{P}^3$. So,  from the above discussion, it is clear that 
+
+Note that each line $l$ in $\mathcal{L}$ has degree 1 in $\mathbb{P}^3$. From the above discussion, for every line $l \in \mathcal{L}$ it is clear that
 		\[
-		\frac{\mathcal{O}_X(1)\cdot l_{\alpha_i,\beta_j}}{10} %= \frac{(l_{\alpha_i,\beta_1} + l_{\alpha_i,\beta_2} + l_{\alpha_i,\beta_3} + l_{\alpha_i,\beta_4})\cdot  l_{\alpha_i,\beta_j} }{10} 
+		\frac{\mathcal{O}_X(1)\cdot l}{10} %= \frac{(l_{\alpha_i,\beta_1} + l_{\alpha_i,\beta_2} + l_{\alpha_i,\beta_3} + l_{\alpha_i,\beta_4})\cdot  l_{\alpha_i,\beta_j} }{10} 
 		= \frac{1}{10}.
 		\]
+
 		Now let $C \subset X$ be any reduced and irreducible curve such that $C \notin \mathcal{L}$ and which passes through some point in the singular locus of 
-		$\mathcal{L}$. By B\'ezout's theorem, we have the following inequality for every line $l \in \mathcal{L}$:
+		$\mathcal{L}$. We will show that the Seshadri ratio given by $C$ is strictly bigger than $\frac{1}{10}$.
+
+  By B\'ezout's theorem, we have the following inequality for every line $l \in \mathcal{L}$:
 		$$2 C \cdot l \ge 2\left( \sum_{p \in l \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right).$$
 
-We now sum such inequalities over all the 48 lines and then group the lines into sets of four lines, in such a way that the sum of each group corresponds to $\mathcal{O}_X(1)$.  Therefore we get
+We now sum such inequalities over all the 48 lines and then group the lines into sets of four lines, in such a way that the sum of the 4 lines in each set is linearly equivalent to $\mathcal{O}_X(1)$.
+Therefore we get
                \begin{eqnarray*}

### 2024-03-19 sc-curve-config.tex
Changes by Krishna-19th March (9:00AM)

@@
 
-In this paper, we continue this study by looking at curve arrangements on arbitrary surfaces.
+In this paper, we continue this study by looking at connected curve arrangements on arbitrary surfaces.
 We prove some analogues of the results in \cite{JP} for arbitrary surfaces.
@@
 for  $1\leq j \leq 4$. Consequently, the sum of these four lines is linearly equivalent to $\mathcal{O}_X(1)$. Similarly, the sum of the four lines 
-$x_0 = \alpha_i x_1 \; \text{and} \; x_2 = \zeta x_3$ is linearly equivalent to $\mathcal{O}_X(1)$. Thus we note that the line 
+$x_0 = \alpha_i x_1 \; \text{and} \; x_2 = \zeta x_3$, 
+for $1\leq i \leq 4$, 
+is linearly equivalent to $\mathcal{O}_X(1)$. Thus we note that the line 
 $x_0 = \zeta x_1 \; \text{and} \; x_2 = \zeta x_3$ is in two different sets of 4 lines each so that the sum of lines in each set is linearly equivalent to $\mathcal{O}_X(1)$.
@@
 
-Note that each line $l$ in $\mathcal{L}$ has degree 1 in $\mathbb{P}^3$. From the above discussion, for every line $l \in \mathcal{L}$ it is clear that
+  We first show that the Seshadri ratio computed by a line in $\mathcal{L}$ is $\frac{1}{10}$. 
+   As mentioned above, every line in $\mathcal{L}$ contains exactly 10 singular points of $\mathcal{L}$. 
+   Note that each line $l$ in $\mathcal{L}$ has degree 1 in $\mathbb{P}^3$.
+   So for every line $l \in \mathcal{L}$, 
 		\[
-		\frac{\mathcal{O}_X(1)\cdot l}{10} %= \frac{(l_{\alpha_i,\beta_1} + l_{\alpha_i,\beta_2} + l_{\alpha_i,\beta_3} + l_{\alpha_i,\beta_4})\cdot  l_{\alpha_i,\beta_j} }{10} 
+		\frac{\mathcal{O}_X(1)\cdot l}{ \sum\limits_{p \in\text{Sing}(\mathcal{L})} \text{mult}_{p} \,l} %= \frac{(l_{\alpha_i,\beta_1} + l_{\alpha_i,\beta_2} + l_{\alpha_i,\beta_3} + l_{\alpha_i,\beta_4})\cdot  l_{\alpha_i,\beta_j} }{10}
 		= \frac{1}{10}.

### 2024-03-19 sc-curve-config.tex
Changes by Krishna-18th March (1;20PM)

@@
 		Let $\mathcal{C}=\{C_1,C_2, \ldots ,C_d\}$ be an arrangement of curves
-		on a smooth projective surface $X$.
+		on a smooth projective surface $X$ such that their union $C_1 \cup C_2 \dots \cup C_d$ is a connected curve in $X$. 
 		We say that $\mathcal{C}$ is a \emph{transversal arrangement}
@@
  \begin{remark} 
-Since each curve in $\mathcal{C}$ is assumed to be linearly equivalent to a fixed divisor $A$, the connectedness hypothesis in 
-Assumption \ref{star1} implies in particular that $C_i\cdot C_j > 0$ for all $1\le i,j \le d$.  Note that the connectedness hypothesis will follow if $A^2 > 0$. 
+Recall that the arrangements we study in this paper are all connected. Since each curve in $\mathcal{C}$ is assumed to be linearly equivalent to a fixed divisor $A$, 
+Assumption \ref{star1} implies in particular that $C_i\cdot C_j > 0$ for all $1\le i,j \le d$.  
  \end{remark}

### 2024-03-19 Response/Response to reviewer.tex
Changes by Krishna-18th March (1;20PM)
Changes by Krishna -19th March (2:21 Almost Final)

@@
 \begin{description}
-\item [Mauscript Number] GMJ 231005 \\
+\item[Paper ID]  GMJ 231005-Subramaniam
+
 \item [Title] Seshadri Constants of Curve Configurations on Surfaces
@@
 \item Following the referee's suggestion, we included the assumption that the arrangement $\mathcal{C}$ is \textit{connected}. 
-We added a remark immediately after Assumption 2.1 mentioning that the connectedness assumption implies that $C_i \cdot C_j > 0$ for all $i,j$.
+This assumption is added in Definition 1.2 itself where transversal arrangements are defined. 
+We also added a remark immediately after Assumption 2.1 mentioning that the connectedness assumption implies that $C_i \cdot C_j > 0$ for all $i,j$.
 
@@
 
-We only needed this assumption while computing the configurational Seshadri constants in Section 2.3. We therefore added the required assumption at the beginning of Seciton 2.3.
+We only needed this assumption while computing the configurational Seshadri constants in Theorems 2.18, 2.19 and 2.21 (Section 2.3).
+We therefore added the required assumption in the statements of Theorem 2.18 and Theorem 2.21.
+(In Theorem 2.19, the hypotheses of Theorem 2.18 are assumed.)
 
@@
 
-\item We have revised Example 2.21 considerably. We shortened it to focus solely on the computation of the Seshadri constant.
+\item We have revised Example 2.21 (new number Example 2.22) considerably. We shortened it to focus solely on the computation of the Seshadri constant.
 \end{itemize}

### 2024-03-19 sc-curve-config.tex
Changes by Krishna -19th March (2:21 Almost Final)

@@
 	\begin{definition}
-		Let $\mathcal{C}=\{C_1,C_2, \ldots ,C_d\}$ be an arrangement of irreducible curves
-		on a smooth projective surface $X$ and singular locus $\text{Sing}(\mathcal{C}).$ Let $L$ be an ample line bundle on $X$.
+		Let $\mathcal{C}=\{C_1,C_2, \ldots ,C_d\}$ be a connected arrangement of irreducible curves
+		on a smooth projective surface $X$ and let $\text{Sing}(\mathcal{C})$ denote the singular locus.
+Let $L$ be an ample line bundle on $X$.
 We define the \textit{configurational Seshadri constant} of $\mathcal{C}$ as
@@
 	\begin{assumption}\label{star1}
-		Let $\mathcal{C}=\{C_1,C_2, \ldots ,C_d\}$, $d\geq 4$ be a connected 
+		Let $\mathcal{C}=\{C_1,C_2, \ldots ,C_d\}$, $d\geq 4$ be a (connected) 
   transversal arrangement of curves 
@@
 We now give some lower bounds on configurational Seshadri constants on ruled surfaces and on surfaces of non-negative Kodaira dimension.	We will 
-work with arrangements of curves satisfying Assumption \ref{star1}. Further, we assume that 
-there is no point where all the curves in $\mathcal{C}$ meet, i.e., $t_d=0.$
+work with arrangements of curves satisfying Assumption \ref{star1}.
 
@@
 	We now give a lower bound on configurational Seshadri constants on surfaces of non-negative Kodaira dimension.
+
 	\begin{theorem}
@@
 
-We now sum such inequalities over all the 48 lines and then group the lines into sets of four lines, in such a way that the sum of the 4 lines in each set is linearly equivalent to $\mathcal{O}_X(1)$.
+We now sum such inequalities over all the 48 lines and then group the lines into sets of four lines as described above, so that that the sum of the four lines in each set is linearly equivalent to $\mathcal{O}_X(1)$.
 Therefore we get
@@
 
- \subsection*{Acknowledgements} We thank the referee for a careful reading of the paper and for giving many corrections and useful comments which substantially improved the paper.
+ \subsection*{Acknowledgements} We thank the referee for a careful reading of the paper, pointing out some corrections and giving several useful comments which substantially improved the paper.
 The first author is partially supported by a grant from Infosys Foundation.

### 2024-03-19 sc-curve-config.tex
Change by me-Added 'connected' in the abstract
Some minor typos fixed in Ex 2.22

@@
 	Let $X$ be a complex nonsingular projective surface and let $L$ be an ample line bundle on $X$.
-We study multi-point Seshadri constants of $L$ at singular points of certain arrangements of curves on $X$.
+We study multi-point Seshadri constants of $L$ at singular points of certain connected arrangements of curves on $X$.
 We pose some questions about such Seshadri constants and prove some results in the case of star arrangements of curves.
@@
 
-We now sum such inequalities over all the 48 lines and then group the lines into sets of four lines as described above, so that that the sum of the four lines in each set is linearly equivalent to $\mathcal{O}_X(1)$.
+We now sum such inequalities over all the 48 lines and then group the lines into sets of four lines as described above, so that the sum of the four lines in each set is linearly equivalent to $\mathcal{O}_X(1)$.
 Therefore we get

### 2024-03-20 sc-curve-config.tex
New version of theorem 2.6-20 March (11:20)

@@
 
+	\textcolor{red}{Let us denote $b_i =  \# \, C_{i} \cap {\rm Sing}(\mathcal{C})$. Note that since our arrangement is connected, $b_i >0$.}
+	\begin{theorem}
+		\label{prop:star} Let $X$ be a nonsingular projective surface and let $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ be a star configuration of curves on $X$ with $d \geq 4$. 
+		Let $L$ be an ample line bundle on $X$
+		such that  $\frac{d\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L-C_i$ is nef for each $i$.   Then 
+		%$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \inf_{C_i}{\frac{L\cdot C_i}{C_i^2(d-1)}}.$$
+		$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \inf_{C_i}{\{\frac{L\cdot C_i}{b_i}\}}.$$
+	\end{theorem}
+	\begin{proof}
+	 Let $\mathcal{P} = \{p_{1}, \ldots, p_{s}\}$ be the singular locus of  $\mathcal{C}$. Note that $p_{1}, \ldots, p_{s}$ are all double points of 
+	  $\mathcal{C}$. Exactly $b_i$ of these points lie on $C_i$. So the Seshadri ratio computed by $C_i$ is precisely 
+	  $ \frac{L\cdot C_i}{b_i}$. %Note that the same ratio is also contributed by each of the curves $C_2,\ldots, C_d$.
+
+	 Suppose that there exists an irreducible and reduced curve $D$, different from $C_{i}$ for $i \in \{1,\ldots, d\}$, having multiplicity $m_{p}(D)$ at each point $p \in \mathcal{P}$ such that
+		%$$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \frac{L\cdot C_1}{C_1^2(d-1)}.$$
+		$$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \inf_{C_i}{\frac{L\cdot C_i}{b_i}}.$$
+This implies
+                $$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \frac{L\cdot C_i}{b_i}.$$ for each $i$. \\
+This gives, after adding over all $i$
+		$$(\triangle) : \quad (L \cdot D)\sum b_i < \left(\sum_{p \in \mathcal{P}} m_{p}(D)\right)\sum L\cdot C_i.$$
+		By B\'ezout's theorem, we obtain
+		\begin{eqnarray*}
+		D\cdot C_i &\geq& m_{p}(D) \cdot m_{p\in C_i \cap \mathcal{C}}C_i  \\
+		&=& m_{p}(D)\cdot b_i.
+		\end{eqnarray*}
+for each $i$. Summing over all $i$, we get	
+		\begin{eqnarray*}
+		 D\cdot (C_{1}+ \ldots + C_{d}) &\geq& \sum_{p \in \mathcal{P}}m_{p}(D)\cdot m_{p}(C_{1}+ \ldots + C_{d})\\
+		&\stackrel{(*)}{\geq}& 2\sum_{p \in \mathcal{P}} m_{p}(D) \\
+		&\stackrel{(\triangle)}{>}& \frac{2(L \cdot D)\sum b_i}{\sum L\cdot C_i},
+		\end{eqnarray*}
+		where $(*)$ comes from the fact that all the singular points of $C_{1}+ \ldots + C_{d}$ are at least double points. Now we use the nefness 
+		of $\frac{d\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L-C_i$ and note the following  inequality: 
+		\[
+		\frac{d\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L\cdot D \geq D\cdot C_i.
+		\] 
+		After adding over all $i=1,...,d$, this leads to the following, 
+		\begin{eqnarray*}
+			\frac{d^2\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L\cdot D &\geq&  D\cdot (C_{1}+ \ldots + C_{d}) > \frac{2(L \cdot D)\sum b_i}{\sum L\cdot C_i} \\
+			%\Rightarrow \frac{d^2C_1^2}{d-1} &>& 2(d-1)C_1^2 \quad \quad \text{(since $L$ is ample)} \\
+			\Rightarrow \left(\frac{d}{d-1} \right)^2 &>& 2 \quad \quad \text{(since $\sum b_i > 0$ and $L$ is ample)}.
+		\end{eqnarray*}
+		This is a contradiction, since $d\geq 4$.
+	\end{proof}
+
 	\begin{theorem}
@@
 	\end{proof}
+
 	\begin{corollary}

### 2024-03-20 sc-curve-config.tex
Generalised version-1-20th March (12:08)

@@
 	%\subsection{General results for any surface}
-	We work with curve configurations on surfaces satisfying the following assumption. 
+
+In this section, we will first prove a result computing Seshadri constants for arbitrary transversal arrangements under a nefness condition. We will then study special cases of this theorem.
+
+We first introduce some notation.
+
+	%\begin{definition}
+		Let $\mathcal{C}$ be a transversal arrangement of curves on a smooth projective surface $X$.
+
+  For each $1\le i \le d$, let $b_i =  \# \, C_{i} \cap {\rm Sing}(\mathcal{C})$. Since our arrangement is connected, $b_i >0$ for all $i$.
+   We define the \emph{base constant} of $\mathcal{C}$ as 
+   $$\text{bs}(\mathcal{C}) = \max\{b_1,\dots, b_d\},$$ i.e., 
+$\text{bs}(\mathcal{C})$		
+  is equal to the maximum number of singular points  of $\mathcal{C}$ that are contained in a single curve $C_{i} \in \mathcal{C}$.
+	%\end{definition}
+
+The following question is a generalization of Question \ref{qn1} to curve arrangements on arbitrary surfaces.
+
+	\begin{question}\label{question}
+		Let $\mathcal{C} =\{C_1,C_2, \ldots ,C_d\}$ be a transversal arrangement of curves on a smooth projective surface $X$. Let $L$ be an ample line bundle on $X$. Is it true that
+		\begin{equation*}\varepsilon(X, L,{\rm Sing}(\mathcal{C})) =  \inf_{C_i}{\left{\frac{L\cdot C_i}{b_i}\}\right}?
+		\end{equation*}
+	\end{question}
+
+By \cite[Example 3.5]{JP}, the above question has a negative answer for the Hesse arrangement of conics 
+in $\mathbb{P}^2$. However it is open for line arrangements in $\mathbb{P}^2$. 
+It is interesting to study the situations in which it is true on arbitrary surfaces.
+
+For an arbitrary curve arrangement $\mathcal{C}$ satisfying Assumption \ref{star1}, the base constant is at most 
+$C_1^2(d-1)$. So the following question arises naturally.
+
+	\begin{question}\label{QuestM}
+		Let $\mathcal{C} =\{C_1,C_2, \ldots ,C_d\}$ be a transversal arrangement of curves on a smooth projective surface $X$
+		satisfying Assumption \ref{star1}. Let  ${\rm Sing}(\mathcal{C})$ denote the singular locus of $\mathcal{C}$ and let $L$ be an ample line bundle on $X$. Is it true that
+		\begin{equation}\label{ques}
+			\varepsilon(X, L,{\rm Sing}(\mathcal{C})) \geq \frac{L \cdot C_1}{C_1^2(d-1)} ?	
+		\end{equation}
+
+	\end{question}
+
+	For star arrangements, the base constant is exactly equal to $C_1^2(d-1)$. We answer this question positively in Corollary \ref{prop:star} for some arrangement.
+
+The following is our main theorem. It gives the value of Seshadri constant for an arbitrary transversal configuration 
+$\mathcal{C} = \{C_1, \dots, C_d\}$
+under a nefness condition.
+
+ %We now show that the lower bound in Question \ref{QuestM} can be achieved by certain star configuration of curves on $X.$	So Question \ref{question} has an affirmative answer for these star arrangements.
+
+	%\textcolor{red}{Let us denote $b_i =  \# \, C_{i} \cap {\rm Sing}(\mathcal{C})$. Note that since our arrangement is connected, $b_i >0$.}
+
+	\begin{theorem}
+		\label{main-theorem} Let $X$ be a nonsingular projective surface and let $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ be a transversal configuration of curves on $X$ with $d \geq 4$. 
+		Let $L$ be an ample line bundle on $X$
+		such that  $\frac{d\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L-C_i$ is nef for each $i$.   Then 
+		%$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \inf_{C_i}{\frac{L\cdot C_i}{C_i^2(d-1)}}.$$
+		$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \inf_{C_i}{\{\frac{L\cdot C_i}{b_i}\}}.$$
+	\end{theorem}
+	\begin{proof}
+	 Let $\mathcal{P} = \{p_{1}, \ldots, p_{s}\}$ be the singular locus of  $\mathcal{C}$. Note that $p_{1}, \ldots, p_{s}$ are all double points of 
+	  $\mathcal{C}$. Exactly $b_i$ of these points lie on $C_i$. So the Seshadri ratio computed by $C_i$ is precisely 
+	  $ \frac{L\cdot C_i}{b_i}$. %Note that the same ratio is also contributed by each of the curves $C_2,\ldots, C_d$.
+
+	 Suppose that there exists an irreducible and reduced curve $D$, different from $C_{i}$ for $i \in \{1,\ldots, d\}$, having multiplicity $m_{p}(D)$ at each point $p \in \mathcal{P}$ such that
+		%$$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \frac{L\cdot C_1}{C_1^2(d-1)}.$$
+		$$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \inf_{C_i}{\frac{L\cdot C_i}{b_i}}.$$
+This implies
+                $$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \frac{L\cdot C_i}{b_i}.$$ for each $i$. \\
+This gives, after adding over all $i$
+		$$(\triangle) : \quad (L \cdot D)\sum b_i < \left(\sum_{p \in \mathcal{P}} m_{p}(D)\right)\sum L\cdot C_i.$$
+		By B\'ezout's theorem, we obtain
+		\begin{eqnarray*}
+		D\cdot C_i &\geq& m_{p}(D) \cdot m_{p\in C_i \cap \mathcal{C}}C_i  \\
+		&=& m_{p}(D)\cdot b_i.
+		\end{eqnarray*}
+for each $i$. Summing over all $i$, we get	
+		\begin{eqnarray*}
+		 D\cdot (C_{1}+ \ldots + C_{d}) &\geq& \sum_{p \in \mathcal{P}}m_{p}(D)\cdot m_{p}(C_{1}+ \ldots + C_{d})\\
+		&\stackrel{(*)}{\geq}& 2\sum_{p \in \mathcal{P}} m_{p}(D) \\
+		&\stackrel{(\triangle)}{>}& \frac{2(L \cdot D)\sum b_i}{\sum L\cdot C_i},
+		\end{eqnarray*}
+		where $(*)$ comes from the fact that all the singular points of $C_{1}+ \ldots + C_{d}$ are at least double points. Now we use the nefness 
+		of $\frac{d\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L-C_i$ and note the following  inequality: 
+		\[
+		\frac{d\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L\cdot D \geq D\cdot C_i.
+		\] 
+		After adding over all $i=1,...,d$, this leads to the following, 
+		\begin{eqnarray*}
+			\frac{d^2\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L\cdot D &\geq&  D\cdot (C_{1}+ \ldots + C_{d}) > \frac{2(L \cdot D)\sum b_i}{\sum L\cdot C_i} \\
+			%\Rightarrow \frac{d^2C_1^2}{d-1} &>& 2(d-1)C_1^2 \quad \quad \text{(since $L$ is ample)} \\
+			\Rightarrow \left(\frac{d}{d-1} \right)^2 &>& 2 \quad \quad \text{(since $\sum b_i > 0$ and $L$ is ample)}.
+		\end{eqnarray*}
+		This is a contradiction, since $d\geq 4$.
+	\end{proof}
+
+Now we will work with configurations satisfying some additional assumptions. More specifically, we will make the following assumption.
+
 	\begin{assumption}\label{star1}
@@
 
-	For star arrangements, the base constant is exactly equal to $C_1^2(d-1)$.
-	We now show that the lower bound in Question \ref{QuestM} can be achieved by certain star configuration of curves on $X.$	So Question \ref{question} has an affirmative answer for these star arrangements.
+	For star arrangements, the base constant is exactly equal to $C_1^2(d-1)$. We answer this question positively in Corollary \ref{prop:star} for some arrangement.
 
-	\textcolor{red}{Let us denote $b_i =  \# \, C_{i} \cap {\rm Sing}(\mathcal{C})$. Note that since our arrangement is connected, $b_i >0$.}
-	\begin{theorem}
-		\label{prop:star} Let $X$ be a nonsingular projective surface and let $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ be a star configuration of curves on $X$ with $d \geq 4$. 
-		Let $L$ be an ample line bundle on $X$
-		such that  $\frac{d\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L-C_i$ is nef for each $i$.   Then 
-		%$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \inf_{C_i}{\frac{L\cdot C_i}{C_i^2(d-1)}}.$$
-		$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \inf_{C_i}{\{\frac{L\cdot C_i}{b_i}\}}.$$
-	\end{theorem}
-	\begin{proof}
-	 Let $\mathcal{P} = \{p_{1}, \ldots, p_{s}\}$ be the singular locus of  $\mathcal{C}$. Note that $p_{1}, \ldots, p_{s}$ are all double points of 
-	  $\mathcal{C}$. Exactly $b_i$ of these points lie on $C_i$. So the Seshadri ratio computed by $C_i$ is precisely 
-	  $ \frac{L\cdot C_i}{b_i}$. %Note that the same ratio is also contributed by each of the curves $C_2,\ldots, C_d$.
+We now prove some corollaries for star arrangements where all the curves are linearly equivalent to a fixed divisor. This answers Question \ref{QuestM} in the affirmative.
 
-	 Suppose that there exists an irreducible and reduced curve $D$, different from $C_{i}$ for $i \in \{1,\ldots, d\}$, having multiplicity $m_{p}(D)$ at each point $p \in \mathcal{P}$ such that
-		%$$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \frac{L\cdot C_1}{C_1^2(d-1)}.$$
-		$$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \inf_{C_i}{\frac{L\cdot C_i}{b_i}}.$$
-This implies
-                $$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \frac{L\cdot C_i}{b_i}.$$ for each $i$. \\
-This gives, after adding over all $i$
-		$$(\triangle) : \quad (L \cdot D)\sum b_i < \left(\sum_{p \in \mathcal{P}} m_{p}(D)\right)\sum L\cdot C_i.$$
-		By B\'ezout's theorem, we obtain
-		\begin{eqnarray*}
-		D\cdot C_i &\geq& m_{p}(D) \cdot m_{p\in C_i \cap \mathcal{C}}C_i  \\
-		&=& m_{p}(D)\cdot b_i.
-		\end{eqnarray*}
-for each $i$. Summing over all $i$, we get	
-		\begin{eqnarray*}
-		 D\cdot (C_{1}+ \ldots + C_{d}) &\geq& \sum_{p \in \mathcal{P}}m_{p}(D)\cdot m_{p}(C_{1}+ \ldots + C_{d})\\
-		&\stackrel{(*)}{\geq}& 2\sum_{p \in \mathcal{P}} m_{p}(D) \\
-		&\stackrel{(\triangle)}{>}& \frac{2(L \cdot D)\sum b_i}{\sum L\cdot C_i},
-		\end{eqnarray*}
-		where $(*)$ comes from the fact that all the singular points of $C_{1}+ \ldots + C_{d}$ are at least double points. Now we use the nefness 
-		of $\frac{d\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L-C_i$ and note the following  inequality: 
-		\[
-		\frac{d\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L\cdot D \geq D\cdot C_i.
-		\] 
-		After adding over all $i=1,...,d$, this leads to the following, 
-		\begin{eqnarray*}
-			\frac{d^2\sum b_i}{(d-1)^2(\sum L\cdot C_i)}L\cdot D &\geq&  D\cdot (C_{1}+ \ldots + C_{d}) > \frac{2(L \cdot D)\sum b_i}{\sum L\cdot C_i} \\
-			%\Rightarrow \frac{d^2C_1^2}{d-1} &>& 2(d-1)C_1^2 \quad \quad \text{(since $L$ is ample)} \\
-			\Rightarrow \left(\frac{d}{d-1} \right)^2 &>& 2 \quad \quad \text{(since $\sum b_i > 0$ and $L$ is ample)}.
-		\end{eqnarray*}
-		This is a contradiction, since $d\geq 4$.
-	\end{proof}
-
-	\begin{theorem}
+	\begin{corollary}
 		\label{prop:star} Let $X$ be a nonsingular projective surface and let $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ be a star configuration of curves on $X$ with $d \geq 4$ such that each $ C_i$ is linearly equivalent to a fixed divisor $A$ on $X$.
@@
 		$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \frac{L\cdot C_1}{C_1^2(d-1)}.$$
-	\end{theorem}
+	\end{corollary}
+
  \begin{proof}
-	 Let $\mathcal{P} = \{p_{1}, \ldots, p_{s}\}$ be the singular locus of  $\mathcal{C}$. Note that $p_{1}, \ldots, p_{s}$ are all double points of 
-	  $\mathcal{C}$. Exactly $C_1^2(d-1)$ of these points lie on $C_1$. So the Seshadri ratio computed by $C_1$ is precisely 
-	  $ \frac{L\cdot C_1}{C_1^2(d-1)}$. Note that the same ratio is also contributed by each of the curves $C_2,\ldots, C_d$.
-
-	 Suppose that there exists an irreducible and reduced curve $D$, different from $C_{i}$ for $i \in \{1,\ldots, d\}$, having multiplicity $m_{p}(D)$ at each point $p \in \mathcal{P}$ such that
-		$$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \frac{L\cdot C_1}{C_1^2(d-1)}.$$
-This gives
-		$$(\triangle) : \quad (L \cdot D)C_1^2(d-1) < \left(\sum_{p \in \mathcal{P}} m_{p}(D)\right)L\cdot C_1.$$
-		By B\'ezout's theorem, we obtain
-		\begin{eqnarray*}
-		D\cdot (C_{1}+ \ldots + C_{d})=d(D\cdot C_1) &\geq& \sum_{p \in \mathcal{P}}m_{p}(D)\cdot m_{p}(C_{1}+ \ldots + C_{d})\\
-		&\stackrel{(*)}{\geq}& 2\sum_{p \in \mathcal{P}} m_{p}(D) \\
-		&\stackrel{(\triangle)}{>}& \frac{2(L \cdot D)C_1^2(d-1)}{L\cdot C_1},
-		\end{eqnarray*}
-		where $(*)$ comes from the fact that all the singular points of $C_{1}+ \ldots + C_{d}$ are at least double points. Now we use the nefness 
-		of $\frac{dC_1^2}{(d-1)(L\cdot C_1)}L-C_1$ and note the following  inequality: 
-		\[
-		\frac{dC_1^2}{(d-1)(L\cdot C_1)}L\cdot D \geq D\cdot C_1.
-		\] 
-		This leads to the following:
-		\begin{eqnarray*}
-			\frac{d^2C_1^2}{(d-1)(L\cdot C_1)}L\cdot D &\geq& d (D\cdot C_1) > \frac{2(d-1)(L\cdot D)C_1^2}{L\cdot C_1} \\
-			\Rightarrow \frac{d^2C_1^2}{d-1} &>& 2(d-1)C_1^2 \quad \quad \text{(since $L$ is ample)} \\
-			\Rightarrow \left(\frac{d}{d-1} \right)^2 &>& 2 \quad \quad \text{(since $C_1^2 = C_1\cdot C_2 > 0$)}.
-		\end{eqnarray*}
-		This is a contradiction, since $d\geq 4$.
+ The proof is immediate from Theorem \ref{main-theorem}.    
  \end{proof}

### 2024-03-20 sc-curve-config.tex
Generalised version-2
Gen_Version (12:41)

@@
 We first introduce some notation. 
-
 	%\begin{definition}
@@
 		Let $\mathcal{C} =\{C_1,C_2, \ldots ,C_d\}$ be a transversal arrangement of curves on a smooth projective surface $X$. Let $L$ be an ample line bundle on $X$. Is it true that
-		\begin{equation*}\varepsilon(X, L,{\rm Sing}(\mathcal{C})) =  \inf_{C_i}{\left{\frac{L\cdot C_i}{b_i}\}\right}?
+		\begin{equation*}
+  \varepsilon(X, L,{\rm Sing}(\mathcal{C})) =  \min_{i}\left\{\frac{L\cdot C_i}{b_i}\right\}?
 		\end{equation*}
@@
 in $\mathbb{P}^2$. However it is open for line arrangements in $\mathbb{P}^2$. 
-It is interesting to study the situations in which it is true on arbitrary surfaces.
+It is interesting to study the situations in which it is true on arbitrary surfaces. Our main theorem answers this question positively under an additional nefness condition.
 
-For an arbitrary curve arrangement $\mathcal{C}$ satisfying Assumption \ref{star1}, the base constant is at most 
-$C_1^2(d-1)$. So the following question arises naturally.
-
-	\begin{question}\label{QuestM}
-		Let $\mathcal{C} =\{C_1,C_2, \ldots ,C_d\}$ be a transversal arrangement of curves on a smooth projective surface $X$
-		satisfying Assumption \ref{star1}. Let  ${\rm Sing}(\mathcal{C})$ denote the singular locus of $\mathcal{C}$ and let $L$ be an ample line bundle on $X$. Is it true that
-		\begin{equation}\label{ques}
-			\varepsilon(X, L,{\rm Sing}(\mathcal{C})) \geq \frac{L \cdot C_1}{C_1^2(d-1)} ?	
-		\end{equation}
-
-	\end{question}
-
-	For star arrangements, the base constant is exactly equal to $C_1^2(d-1)$. We answer this question positively in Corollary \ref{prop:star} for some arrangement.
-
-The following is our main theorem. It gives the value of Seshadri constant for an arbitrary transversal configuration 
-$\mathcal{C} = \{C_1, \dots, C_d\}$
-under a nefness condition.
+%The following is our main theorem. It gives the value of Seshadri  constant for an arbitrary transversal configuration  $\mathcal{C} = \{C_1, \dots, C_d\}$ under a nefness condition.
 
@@
 
+\begin{remark}
+Several authors have studied multi-point Seshadri constants on surfaces; for a sample of results, see \cite{B,HM, HR, PR, RR, SS}. 
+Many of these results consider general points. 
+Theorem \ref{main-theorem} gives a computation of Seshadri constants at \textit{special} points. 
+\end{remark}
+
 Now we will work with configurations satisfying some additional assumptions. More specifically, we will make the following assumption.
@@
  \end{remark}
-	\begin{definition}
-		Let $\mathcal{C}$ be a transversal arrangement of curves on a smooth projective surface $X$
-		satisfying Assumption \ref{star1}. Then we define the \emph{base constant} of $\mathcal{C}$ as 
-		$${\rm bs}(\mathcal{C}) := {\rm max} \{t \, | \, t = \# \, C_{i} \cap {\rm Sing}(\mathcal{C}), \, C_{i} \in \mathcal{C}\},$$
-		i.e., ${\rm bs}(\mathcal{C})$ is equal to the maximum number of singular points  of $\mathcal{C}$ that are contained in a single curve $C_{i} \in \mathcal{C}$.
-	\end{definition}
-
-The following question is a generalization of Question \ref{qn1} to curve arrangements on arbitrary surfaces.
-
-	\begin{question}\label{question}
-		Let $\mathcal{C} =\{C_1,C_2, \ldots ,C_d\}$ be a transversal arrangement of curves on a smooth projective surface $X$
-		satisfying Assumption \ref{star1}. Let $L$ be an ample line bundle on $X$. Is it true that
-		\begin{equation*}\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \frac{L \cdot C_1}{{\rm bs}(\mathcal{C})}?
-		\end{equation*}
-	\end{question}
-
-By \cite[Example 3.5]{JP}, the above question has a negative answer for the Hesse arrangement of conics 
-in $\mathbb{P}^2$. However it is open for line arrangements in $\mathbb{P}^2$. 
-It is interesting to study the situations in which it is true on arbitrary surfaces.
 
@@
 
-	For star arrangements, the base constant is exactly equal to $C_1^2(d-1)$. We answer this question positively in Corollary \ref{prop:star} for some arrangement.
+	For star arrangements, the base constant is exactly equal to $C_1^2(d-1)$. We answer this question positively in the following  corollaries for some arrangements.
 
-We now prove some corollaries for star arrangements where all the curves are linearly equivalent to a fixed divisor. This answers Question \ref{QuestM} in the affirmative.
+%We now prove some corollaries for star arrangements where all the curves are linearly equivalent to a fixed divisor. This answers Question \ref{QuestM} in the affirmative.
 
@@
 
-\begin{remark}
-Several authors have studied multi-point Seshadri constants on surfaces; for a sample of results, see \cite{B,HM, HR, PR, RR, SS}. 
-Many of these results consider general points. 
-Theorem \ref{prop:star} gives a computation of Seshadri constants at \textit{special} points. 
-\end{remark}
-
-The proof of Theorem \ref{prop:star} shows that for an arbitrary arrangement, not necessarily a star arrangement, we have the following lower and upper bounds for the Seshadri constants.
+The proof of Theorem \ref{main-theorem} shows that for arrangements
+satisfying Assumption \ref{star1}, we have the following lower and upper bounds for the Seshadri constants.
 
@@
 \begin{proof}
-The inequality $\frac{L\cdot C_1}{C_1^2(d-1)} \le \varepsilon(X, L,{\rm Sing}(\mathcal{C}))$ follows from the proof of Theorem \ref{prop:star}.
-Note that for any reduced and irreducible curve $D$ which is not in $\mathcal{C}$, we showed that the Seshadri ratio is at least $\frac{L\cdot C_1}{C_1^2(d-1)}$ and this part does not use the fact that $\mathcal{C}$ is a star arrangement.
+
+Note that the hypotheses of Theorem \ref{main-theorem} hold here. 
+ For any reduced and irreducible curve $D$ which is not in $\mathcal{C}$, we showed in the proof of Theorem \ref{main-theorem}
+that the Seshadri ratio is at least $\frac{L\cdot C_1}{C_1^2(d-1)}$. 
+So we obtain $\frac{L\cdot C_1}{C_1^2(d-1)} \le \varepsilon(X, L,{\rm Sing}(\mathcal{C}))$.
 
@@
 
+We note that the nefness assumption of Theorem \ref{main-theorem} does not hold here. Indeed, $b_i = 8$ for each $1 \le i \le 12$. So the divisor 
+$\left(\frac{12(b_1+\dots + b_{12})}{11*11*24}\right)L - C_1$ is not nef because 
+$b_1+\dots + b_{12} < 4*11^2$.
+
+However, Corollary \ref{cor-main} does apply in this case. 
 It is easy to see that $\frac{24}{11}L - C_1$ is nef. 
@@
 This shows that the inequalities in Corollary \ref{cor-main} are strict, in general.
-In particular,  Theorem \ref{prop:star} does not hold in this case.
+In particular,  Corollary \ref{prop:star} does not hold in this case.
 Note that $\mathcal{C}$ is not a star arrangement.

### 2024-03-20 Response/Response to reviewer.tex
Change by me-Added 'connected' in the abstract
Generalised version-Almost final-1 changes by Krishna

@@
 We thank the referee for carefully reading the manuscript and suggesting 
-many useful changes and also for pointing out an error in the Assumption 2.1 which leads to 
+many useful changes including a valuable suggestion to remove the hypothesis that all the curves in $\mathcal{C}$ are linearly equivalent to a fixed divisor.
+We were able to do this and our main theorem now (Theorem 2.2 in the new version) is a general result without the old assumption.
+
+We also thank the referee for pointing out an error in  Assumption 2.1 which leads to 
 ambiguities at several places. We fixed this error by assuming that the arrangement is connected.
 
-We also agree with the referee that Example 2.21 can be shortened and it is better to 
+We  agree with the referee that Example 2.22 (in the new version)  can be shortened and it is better to solely 
 focus on the computation of Seshadri constants.
+
+All the suggestions substantially improved the paper and we are grateful to the referee for giving these suggestions.
 
@@
 \begin{itemize}
-\item Following the referee's suggestion, we included the assumption that the arrangement $\mathcal{C}$ is \textit{connected}. 
+
+\item As the referee mentioned correctly, the proof of the main theorem in the original version did not really need the assumption that all the curves are linearly equivalent to a fixed divisor.
+We removed this hypothesis and the hypothesis that $\mathcal{C}$ is a star arrangement and re-wrote the proof in the more general setting.
+The earlier results were retained as corollaries.
+
+We also modified some of the questions we asked to fit the more general setting of the new version.
+
+\item Following the referee's suggestion, we included the assumption that the arrangement $\mathcal{C}$ is \textit{connected} throughout. 
 This assumption is added in Definition 1.2 itself where transversal arrangements are defined.
-We also added a remark immediately after Assumption 2.1 mentioning that the connectedness assumption implies that $C_i \cdot C_j > 0$ for all $i,j$.
 
-\item We also removed the unnecessary assumption that all the curves do not meet at any point. Referee correctly noted that this is not necessary for the main results.
+%We also added a remark immediately after Assumption 2.1 mentioning that the connectedness assumption implies that $C_i \cdot C_j > 0$ for all $i,j$.
 
-We only needed this assumption while computing the configurational Seshadri constants in Theorems 2.18, 2.19 and 2.21 (Section 2.3).
+\item We  removed the unnecessary assumption that all the curves do not meet at any point. Referee correctly noted that this is not necessary for the main results.
+
+We only needed this assumption while computing the configurational Seshadri constants in  Theorems 2.18, 2.19 and 2.21 (in the new version) .
 We therefore added the required assumption in the statements of Theorem 2.18 and Theorem 2.21.
@@
 %from the connectedness of the arrangement.
-\item We retained the condition that all curves in our arrangements are linearly equivalent to a specific divisor.
-Many of the results and questions we state depend on this assumption.
-So removing this assumption will require a substantial re-working of the paper.
 
@@
 
-\item We have revised Example 2.21 (new number Example 2.22) considerably. We shortened it to focus solely on the computation of the Seshadri constant.
+\item We  revised Example 2.22 (in the new version) considerably. We shortened it to focus solely on the computation of the Seshadri constant.
 \end{itemize}

### 2024-03-20 sc-curve-config.tex
Generalised version-Almost final-1 changes by Krishna

@@
 We study multi-point Seshadri constants of $L$ at singular points of certain connected arrangements of curves on $X$.
-We pose some questions about such Seshadri constants and prove some results in the case of star arrangements of curves.
+We pose some questions about such Seshadri constants and prove results in many cases, including star arrangements of curves.
 We also study the configurational Seshadri constants for curve arrangements on surfaces and compare them with the usual Seshadri constants.
@@
 		\begin{question}\label{qn1}
-		Let $x_1, \cdots, x_r \subset \mathbb{P}^2$ be the set of singular points in a configuration of lines  which is not a pencil of lines.
+		Let $x_1, \cdots, x_r \in \mathbb{P}^2$ be the set of singular points in a configuration of lines  which is not a pencil of lines.
 Let $k$ denote the maximum number of points which lie on a line.
@@
 
-The main configurations considered in this paper are the \textit{star configurations}. We make the following definition: 
+One class of arrangements studied in this paper are 
+ natural analogues of the classical star arrangements of lines on $\mathbb{P}^2$. 
+We make the following definition.
+
 \begin{definition} Let $X$ be a nonsingular projective surface.  
@@
 
-In Section \ref{main}, we prove our main result (Theorem \ref{prop:star}) for star arrangements of curves on arbitrary surfaces. 
+In Section \ref{main}, we prove one of our main results (Theorem \ref{main-theorem})
+for a transversal arrangement $\mathcal{C}$ of curves on a smooth projective surface under a nefness condition.
+We will then assume that all curves in $\mathcal{C}$ are linearly equivalent to a fixed divisor and prove some results for such configurations using Theorem \ref{main-theorem}.
+The main result in this set-up is Corollary \ref{prop:star}.
+
 In Section \ref{ruled}, we consider some examples on ruled surfaces.
@@
 In Section \ref{bounds}, we give lower bounds for configurational Seshadri constants for curve arrangements on surfaces.
-Finally, we give an example of a computation of multi-point Seshadri constant at the singular locus of an arrangement of curves on a K3 surface.
+
+Finally, we give an example (Example \ref{K3}) of a computation of multi-point the Seshadri constant at the singular locus of an arrangement of curves on a K3 surface.
+In this example, the nefness hypothesis of Theorem \ref{main-theorem} is not true but the conclusion about the Seshadri constant still holds.
 
@@
 		\begin{equation*}
-  \varepsilon(X, L,{\rm Sing}(\mathcal{C})) =  \min_{i}\left\{\frac{L\cdot C_i}{b_i}\right\}?
+  \varepsilon(X, L,{\rm Sing}(\mathcal{C})) =  \min_{1\le i \le d}\left\{\frac{L\cdot C_i}{b_i}\right\}?
 		\end{equation*}
@@
 		%$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \inf_{C_i}{\frac{L\cdot C_i}{C_i^2(d-1)}}.$$
-		$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \inf_{C_i}{\{\frac{L\cdot C_i}{b_i}\}}.$$
+		$$\varepsilon(X, L,{\rm Sing}(\mathcal{C})) = \min_{1\le i\le d}
+  {\left\{\frac{L\cdot C_i}{b_i}\right\}}.$$
 	\end{theorem}
 	\begin{proof}
-	 Let $\mathcal{P} = \{p_{1}, \ldots, p_{s}\}$ be the singular locus of  $\mathcal{C}$. Note that $p_{1}, \ldots, p_{s}$ are all double points of 
-	  $\mathcal{C}$. Exactly $b_i$ of these points lie on $C_i$. So the Seshadri ratio computed by $C_i$ is precisely 
+	 Let $\mathcal{P} = \{p_{1}, \ldots, p_{s}\}$ be the singular locus of  $\mathcal{C}$.
+For each $i$, exactly $b_i$ points in $\mathcal{P}$  lie on $C_i$.
+Since each $C_i$ is smooth, the Seshadri ratio computed by $C_i$ is precisely
 	  $ \frac{L\cdot C_i}{b_i}$. %Note that the same ratio is also contributed by each of the curves $C_2,\ldots, C_d$.
 
-	 Suppose that there exists an irreducible and reduced curve $D$, different from $C_{i}$ for $i \in \{1,\ldots, d\}$, having multiplicity $m_{p}(D)$ at each point $p \in \mathcal{P}$ such that
+  We will now show that the Seshadri ratio given by any curve $D$ not in $\mathcal{C}$ is at least $\min_{1\le i\le d}
+  {\left\{\frac{L\cdot C_i}{b_i}\right\}}$.
+
+	 Suppose that there exists an irreducible and reduced curve $D\notin \mathcal{C}$ having multiplicity $m_{p}(D)$ at each point $p \in \mathcal{P}$ such that $D \cap \mathcal{P} \ne \emptyset$ and 
 		%$$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \frac{L\cdot C_1}{C_1^2(d-1)}.$$
-		$$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \inf_{C_i}{\frac{L\cdot C_i}{b_i}}.$$
-This implies
-                $$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \frac{L\cdot C_i}{b_i}.$$ for each $i$. \\
-This gives, after adding over all $i$
+		$$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \min_{1\le i \le d}\left\{\frac{L\cdot C_i}{b_i}\right\}.$$
+So 
+                $$b_i(L \cdot D)  < (L\cdot C_i) \sum_{p \in \mathcal{P}} m_{p}(D).$$ for each $i$. 
+Adding over all $i$, we have 
 		$$(\triangle) : \quad (L \cdot D)\sum b_i < \left(\sum_{p \in \mathcal{P}} m_{p}(D)\right)\sum L\cdot C_i.$$
-		By B\'ezout's theorem, we obtain
-		\begin{eqnarray*}
-		D\cdot C_i &\geq& m_{p}(D) \cdot m_{p\in C_i \cap \mathcal{C}}C_i  \\
-		&=& m_{p}(D)\cdot b_i.
-		\end{eqnarray*}
-for each $i$. Summing over all $i$, we get	
+		By B\'ezout's theorem applied to $D$ and $C_1+\dots+C_d$, we obtain
+		%\begin{eqnarray*}
+		%D\cdot C_i &\geq& m_{p}(D) \cdot m_{p\in C_i \cap \mathcal{C}}C_i  \\
+		%&=& m_{p}(D)\cdot b_i.
+		%\end{eqnarray*}
+%for each $i$. Summing over all $i$, we get	
 		\begin{eqnarray*}
@@
 
-Now we will work with configurations satisfying some additional assumptions. More specifically, we will make the following assumption.
+Now we will work with configurations satisfying some additional assumptions. Specifically, we will make the following assumption.
 
@@
 
-	For star arrangements, the base constant is exactly equal to $C_1^2(d-1)$. We answer this question positively in the following  corollaries for some arrangements.
+	For star arrangements, the base constant is exactly equal to $C_1^2(d-1)$. We answer the above question positively for some arrangements  in the following  corollaries
 
@@
 
-	We now construct examples such that the conclusion of Theorem \ref{prop:star} holds, even without the nefness condition in the hypothesis.
+	We now construct examples such that the conclusion of Corollary \ref{prop:star} holds, even without the nefness condition in the hypothesis.
 We construct these examples by obtaining transversal arrangement of curves on rational ruled surfaces coming from line arrangements in $\mathbb{P}^2.$
@@
 
-	In the next example, the conclusion of Theorem \ref{prop:star} holds, even without the nefness condition in the hypothesis. 
+	In the next example, the conclusion of Corollary \ref{prop:star} holds, even without the nefness condition in the hypothesis. 
 	\begin{example}\label{nef}
@@
 
- Let $L=C_0+3f$ be an ample line bundle on $X.$ Then we have $$(5C_1^2/4L\cdot C_1))L-C_1= \frac{1}{6}(-C_0+3f),$$ which is not nef as $(-C_0+3f)\cdot f = -1 < 0.$ Hence the nefness hypothesis in Theorem \ref{prop:star} fails.
+ Let $L=C_0+3f$ be an ample line bundle on $X.$ Then we have $$(5C_1^2/4L\cdot C_1))L-C_1= \frac{1}{6}(-C_0+3f),$$ which is not nef as $(-C_0+3f)\cdot f = -1 < 0.$ Hence the nefness hypothesis in Corollary \ref{prop:star} fails.
 
@@
 	\begin{example}
-		In Theorem \ref{prop:star}, we considered a \emph{star} configuration $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ with $d \geq 4$ such that $ C_i \in |A|$ for all $i$, where $A$ was a fixed divisor on $X$.
+		In Corollary \ref{prop:star}, we considered a \emph{star} configuration $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ with $d \geq 4$ such that $ C_i \in |A|$ for all $i$, where $A$ was a fixed divisor on $X$.
 We saw that for an ample line bundle $L$  on $X$, if
@@
 
-We end with an example of a configuration of lines on a K3 surface in $\mathbb{P}^3$. Though it does
-not fit in the situation studied in this paper (since the curves in the arrangement are not
-linearly equivalent to each other), it gives an interesting computation of a multi-point Seshadri
-constant on a K3 surface.
+We end with an example of a configuration of lines on a K3 surface in $\mathbb{P}^3$. In this example, the nefness hypothesis of Theorem \ref{main-theorem} is not satisfied, but the conclusions hold. 
+%Though it does
+%not fit in the situation studied in this paper (since the curves in the arrangement are not
+%linearly equivalent to each other), it gives an interesting computation of a multi-point Seshadri
+%constant on a K3 surface.
 
-\begin{example}
+\begin{example}\label{K3}
 		Let $X \subset \mathbb{P}^3$ be a Fermat quartic defined by the vanishing locus of $x_0^4 + x_1^4 + x_2^4 + x_3^4$, where $x_0, \ldots, x_3$ are the coordinates of $\mathbb{P}^3$. 
@@
 In fact, we claim that
-		\[
+		\begin{equation}\label{2.22}
 		\varepsilon(X, \mathcal{O}_X(1), \text{Sing}(\mathcal{L})) = \frac{1}{10}.
-		\]
+	\end{equation}
 
-  We first show that the Seshadri ratio computed by a line in $\mathcal{L}$ is $\frac{1}{10}$. 
+Note that Theorem \ref{main-theorem} predicts that the Seshadri constant is indeed $\frac{1}{10}$, though that theorem cannot be applied here. This is because 
+$d=48, b_1=\dots = b_{48} = 10$ and $L\cdot l_i = 1$ for every $i$. The divisor
+in question is not nef, as can be seen by intersecting with $l_i$.
+
+  To prove \eqref{2.22}, we first show that the Seshadri ratio computed by a line in $\mathcal{L}$ is $\frac{1}{10}$. 
    As mentioned above, every line in $\mathcal{L}$ contains exactly 10 singular points of $\mathcal{L}$. 
@@
 		\]
-		This completes the proof of the claim.
+		This completes the proof of the equality \eqref{2.22}.
 

### 2024-03-20 sc-curve-config.tex
Changes by Krishna-Almost Final-1

@@
 in $\mathbb{P}^2$. However it is open for line arrangements in $\mathbb{P}^2$. 
-It is interesting to study the situations in which it is true on arbitrary surfaces. Our main theorem answers this question positively under an additional nefness condition.
+It is interesting to study the situations in which it is true on arbitrary surfaces. Our main theorem below answers this question positively under an additional nefness condition.
 
@@
 
-	For star arrangements, the base constant is exactly equal to $C_1^2(d-1)$. We answer the above question positively for some arrangements  in the following  corollaries
+	For star arrangements, the base constant is exactly equal to $C_1^2(d-1)$. We answer the above question positively for some arrangements below.
 
@@
  \begin{proof}
- The proof is immediate from Theorem \ref{main-theorem}.    
- \end{proof}
+Under the given hypotheses, we have $b_i = C_1^2(d-1)$  and $L\cdot C_i = L\cdot L_1$
+for all $i$. 
+The proof is now immediate from Theorem \ref{main-theorem}.    
+ \end{proof} This immediately gives the following.
 
@@
 
-The proof of Theorem \ref{main-theorem} shows that for arrangements
-satisfying Assumption \ref{star1}, we have the following lower and upper bounds for the Seshadri constants.
+The proof of Theorem \ref{main-theorem} can be modified to show that for arrangements
+satisfying Assumption \ref{star1} which are not star arrangements, we still have the following lower and upper bounds for the Seshadri constants.
 
@@
 
-Note that the hypotheses of Theorem \ref{main-theorem} hold here. 
- For any reduced and irreducible curve $D$ which is not in $\mathcal{C}$, we showed in the proof of Theorem \ref{main-theorem}
-that the Seshadri ratio is at least $\frac{L\cdot C_1}{C_1^2(d-1)}$. 
-So we obtain $\frac{L\cdot C_1}{C_1^2(d-1)} \le \varepsilon(X, L,{\rm Sing}(\mathcal{C}))$.
+Let  $D \notin \mathcal{C}$ be 
+a reduced and irreducible curve which contains some points of the singular locus $\mathcal{P}$ of $\mathcal{C}$. Essentially following the proof of Theorem \ref{main-theorem}, we can show that 
+$$ \frac{L\cdot C_1}{C_1^2(d-1)} \le \frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)}.$$
+
+%$D \notin \mathcal{C}$, we showed in the proof of Theorem \ref{main-theorem} that the Seshadri ratio is at least $\frac{L\cdot C_1}{C_1^2(d-1)}$. 
+%So we obtain $\frac{L\cdot C_1}{C_1^2(d-1)} \le \varepsilon(X, L,{\rm Sing}(\mathcal{C}))$.
+
+Indeed, suppose that the above inequality does not hold. 
+As in the proof of Theoerem \ref{main-theorem}, B\'ezout's theorem applied to $D$ and $C_1+\dots+C_d$ gives
+
+$$		 D\cdot (C_{1}+ \ldots + C_{d}) \ge  
+\frac{2(d-1)(L \cdot D)C_1^2}{L\cdot C_1}.$$
+
+		Now we use the nefness of 
+  $\frac{dC_1^2}{(d-1)(L\cdot C_1)}L-C_1$ and obtain a contradiction exactly as in the proof of Theorem \ref{main-theorem}. We omit the details since the argument is identical.
 

### 2024-03-21 Response/Response to reviewer.tex
Final-after-1st-revision-1

@@
 many useful changes including a valuable suggestion to remove the hypothesis that all the curves in $\mathcal{C}$ are linearly equivalent to a fixed divisor.
-We were able to do this and our main theorem now (Theorem 2.2 in the new version) is a general result without the old assumption.
+We were able to do this and our main theorem now (Theorem 2.2 in the new version) is a more general result without the old assumption.
 
@@
 
-We  agree with the referee that Example 2.22 (in the new version)  can be shortened and it is better to solely 
-focus on the computation of Seshadri constants.
+We  agree with the referee that Example 2.22 (in the new version)  can be shortened and it is better to  
+focus solely on the computation of Seshadri constants.
 
-All the suggestions substantially improved the paper and we are grateful to the referee for giving these suggestions.
+All these suggestions substantially improved the paper and we are grateful to the referee for them.
 

### 2024-03-21 sc-curve-config.tex
Final-after-1st-revision-1

@@
 
-Finally, we give an example (Example \ref{K3}) of a computation of multi-point the Seshadri constant at the singular locus of an arrangement of curves on a K3 surface.
+Finally, we give an example (Example \ref{K3}) of a computation of the multi-point Seshadri constant at the singular locus of an arrangement of curves on a K3 surface.
 In this example, the nefness hypothesis of Theorem \ref{main-theorem} is not true but the conclusion about the Seshadri constant still holds.
@@
 
-  For each $1\le i \le d$, let $b_i =  \# \, C_{i} \cap {\rm Sing}(\mathcal{C})$. Since our arrangement is connected, $b_i >0$ for all $i$.
+  For each $1\le i \le d$, let $b_i =  \# \, C_{i} \cap {\rm Sing}(\mathcal{C})$. Since $\mathcal{C}$ is connected, $b_i >0$ for all $i$.
    We define the \emph{base constant} of $\mathcal{C}$ as 
@@
 By \cite[Example 3.5]{JP}, the above question has a negative answer for the Hesse arrangement of conics 
-in $\mathbb{P}^2$. However it is open for line arrangements in $\mathbb{P}^2$. 
+in $\mathbb{P}^2$; see Example \ref{hesse}. However it is open for line arrangements in $\mathbb{P}^2$. 
 It is interesting to study the situations in which it is true on arbitrary surfaces. Our main theorem below answers this question positively under an additional nefness condition.
@@
 		$$\frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)} < \min_{1\le i \le d}\left\{\frac{L\cdot C_i}{b_i}\right\}.$$
-So 
-                $$b_i(L \cdot D)  < (L\cdot C_i) \sum_{p \in \mathcal{P}} m_{p}(D).$$ for each $i$. 
+So for each $1 \le i \le d$, we have 
+                $$b_i(L \cdot D)  < (L\cdot C_i) \sum_{p \in \mathcal{P}} m_{p}(D).$$
+
 Adding over all $i$, we have 
-		$$(\triangle) : \quad (L \cdot D)\sum b_i < \left(\sum_{p \in \mathcal{P}} m_{p}(D)\right)\sum L\cdot C_i.$$
+		$$(\triangle) : \quad (L \cdot D)\sum_{i=1}^d b_i < \left(\sum_{p \in \mathcal{P}} m_{p}(D)\right)\sum_{i=1}^d L\cdot C_i.$$
 		By B\'ezout's theorem applied to $D$ and $C_1+\dots+C_d$, we obtain
@@
 For an arbitrary curve arrangement $\mathcal{C}$ satisfying Assumption \ref{star1}, the base constant is at most 
-$C_1^2(d-1)$. So the following question arises naturally.
+$C_1^2(d-1)$. So the following question arises naturally from
+Question \ref{question}.
 
@@
  \begin{proof}
-Under the given hypotheses, we have $b_i = C_1^2(d-1)$  and $L\cdot C_i = L\cdot L_1$
+Under the given hypotheses, we have $b_i = C_1^2(d-1)$  and $L\cdot C_i = L\cdot C_1$
 for all $i$. 
@@
 The proof of Theorem \ref{main-theorem} can be modified to show that for arrangements
-satisfying Assumption \ref{star1} which are not star arrangements, we still have the following lower and upper bounds for the Seshadri constants.
+satisfying Assumption \ref{star1} which are not necessarily star arrangements, we still have the following lower and upper bounds for the Seshadri constants.
 
@@
 Indeed, suppose that the above inequality does not hold. 
-As in the proof of Theoerem \ref{main-theorem}, B\'ezout's theorem applied to $D$ and $C_1+\dots+C_d$ gives
+As in the proof of Theorem \ref{main-theorem}, B\'ezout's theorem applied to $D$ and $C_1+\dots+C_d$ gives
 
@@
 
-\begin{example}
+\begin{example}\label{hesse}
 Consider the Hesse arrangement $\mathcal{C} = \{C_1, \ldots, C_{12}\}$  of conics in $\mathbb{P}^2$
@@
 
-We end with an example of a configuration of lines on a K3 surface in $\mathbb{P}^3$. In this example, the nefness hypothesis of Theorem \ref{main-theorem} is not satisfied, but the conclusions hold. 
+We end with an example of a configuration of lines on a K3 surface in $\mathbb{P}^3$. In this example, the nefness hypothesis of Theorem \ref{main-theorem} is not satisfied, but the conclusion holds. 
 %Though it does
@@
 
-Note that Theorem \ref{main-theorem} predicts that the Seshadri constant is indeed $\frac{1}{10}$, though that theorem cannot be applied here. This is because 
-$d=48, b_1=\dots = b_{48} = 10$ and $L\cdot l_i = 1$ for every $i$. The divisor
-in question is not nef, as can be seen by intersecting with $l_i$.
+Note that Theorem \ref{main-theorem} predicts that the Seshadri constant is indeed $\frac{1}{10}$, though  it cannot be applied here. This is because 
+$d=48, b_i = 10$ and $L\cdot l_i = 1$ for every $i$. So the divisor which appears in the statement of Theorem \ref{main-theorem}
+is not nef, as can be seen by intersecting with $l_i$.
 
@@
 
- \subsection*{Acknowledgements} We thank the referee for a careful reading of the paper, pointing out some corrections and giving several useful comments which substantially improved the paper.
+ \subsection*{Acknowledgements} We thank the referee for a careful reading of the paper, pointing out some corrections and giving several useful suggestions which substantially improved the paper.
 The first author is partially supported by a grant from Infosys Foundation.

### 2024-03-21 sc-curve-config.tex
Final-version-after-1st-review

@@
 		$$(\triangle) : \quad (L \cdot D)\sum_{i=1}^d b_i < \left(\sum_{p \in \mathcal{P}} m_{p}(D)\right)\sum_{i=1}^d L\cdot C_i.$$
+
   By B\'ezout's theorem applied to $D$ and $C_1+\dots+C_d$, we obtain
@@
 		\]
+
 		After adding over all $i=1,...,d$, this leads to the following, 
@@
 The proof of Theorem \ref{main-theorem} can be modified to show that for arrangements
-satisfying Assumption \ref{star1} which are not necessarily star arrangements, we still have the following lower and upper bounds for the Seshadri constants.
+satisfying Assumption \ref{star1}, which are not necessarily star arrangements, we still have the following lower and upper bounds for the Seshadri constants.
 

### 2024-04-30 sc-curve-config.tex
Some changes by Krishna after result from Glasgow

@@
 
-	In \cite{JP}, the authors also study the multi-point Seshadri constants of $\mathcal{O}_{\mathbb{P}^{2}_{\mathbb{C}}}(1)$ centered at singular loci of certain curve arrangements $\mathcal{C}$ in ${\mathbb{P}^{2}_{\mathbb{C}}}$ using a combinatorial invariant called the  \textit{configurational Seshadri constant of $\mathcal{C}$}.
-They give lower bounds for the configurational Seshadri constants of $\mathcal{O}_{\mathbb{P}^{2}_{\mathbb{C}}}(1)$ and also provide some actual values of the multi-point Seshadri constants for some classes of curve arrangements, comparing them with their associated configurational Seshadri constants.
+    	In \cite{JP}, the authors also study the multi-point Seshadri constants of $\mathcal{O}_{\mathbb{P}^{2}}(1)$ centered at singular loci of certain curve arrangements $\mathcal{C}$ in $\mathbb{P}^{2}$ using a combinatorial invariant called the  \textit{configurational Seshadri constant of $\mathcal{C}$}.
+They give lower bounds for the configurational Seshadri constants of $\mathcal{O}_{\mathbb{P}^{2}}(1)$ and also provide some actual values of the multi-point Seshadri constants for some classes of curve arrangements, comparing them with their associated configurational Seshadri constants.
 
@@
 \begin{example}
-In \cite[Example 3.1]{JP}, it was shown that for a Hirzebruch quasi-pencil $\mathcal{H}$ of $k\geq 4$ lines in $\mathbb{P}^2_{\mathbb{C}}$ with $t_{k-1}=1$ and $t_2=k-1$, the multi-point Seshadri constant $\varepsilon(\mathbb{P}^2_{\mathbb{C}}, \mathcal{O}_{\mathbb{P}^2_{\mathbb{C}}}(1),{\rm Sing}(\mathcal{H}))$ is strictly smaller than its configurational value $\varepsilon_{\mathcal{H}}(\mathcal{O}_{\mathbb{P}^2_{\mathbb{C}}}(1)).$ We can obtain a configuration $\mathcal{H}'$ on a rational ruled surface $X_e$ with $e=k+1$, as a pullback of the Hirzebruch quasi-pencil $\mathcal{H}$, using the construction mentioned above.
+In \cite[Example 3.1]{JP}, it was shown that for a Hirzebruch quasi-pencil $\mathcal{H}$ of $k\geq 4$ lines in $\mathbb{P}^2$ with $t_{k-1}=1$ and $t_2=k-1$, the multi-point Seshadri constant $\varepsilon(\mathbb{P}^2, \mathcal{O}_{\mathbb{P}^2}(1),{\rm Sing}(\mathcal{H}))$ is strictly smaller than its configurational value $\varepsilon_{\mathcal{H}}(\mathcal{O}_{\mathbb{P}^2}(1)).$ We can obtain a configuration $\mathcal{H}'$ on a rational ruled surface $X_e$ with $e=k+1$, as a pullback of the Hirzebruch quasi-pencil $\mathcal{H}$, using the construction mentioned above.
 The configuration $\mathcal{H}'$ consists of $k \geq 4$ curves say $C_{1}, \ldots, C_{k}$, with $t_{k-1}=e$, $t_2=(k-1)e$ and $ C_i \in |C_0+ef|$ for all $i.$ Let $L=C_0+(e+1)f$ be an ample line bundle on $X_e.$
@@
 \bibitem{Pok1}	P. Pokora, Harbourne constants and arrangements of lines on smooth hypersurfaces in
-$\mathbb{P}_{\mathbb{C}}^3$,  Taiwanese J. Math., \textbf{20}, No. 1 (2016), 25--31.
+$\mathbb{P}^3$,  Taiwanese J. Math., \textbf{20}, No. 1 (2016), 25--31.
 

### 2024-07-18 sc-curve-config.tex
Final Changes before publication
Page 2 line 4: Replaced X and L with P^2 and O(1)

@@
 For example, if the points are collinear then
-	$\varepsilon(X,L,x_1,\ldots,x_r) = \frac{1}{r}$.
+	$\varepsilon(\mathbb{P}^2,\mathcal{O}_{\mathbb{P}^2}(1),x_1,\ldots,x_r) = \frac{1}{r}$.
 
@@
 
- \subsection*{Acknowledgements} We thank the referee for a careful reading of the paper, pointing out some corrections and giving several useful suggestions which substantially improved the paper.
-The first author is partially supported by a grant from Infosys Foundation.
+ \subsection*{Acknowledgements} The first author is partially supported by a grant from Infosys Foundation.
 
